---
title: "Test Harvest Control Rule with a Butterfish-like stock"
author: "Sarah Gaichas"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(wham)
library(SPASAM.MSE) # build my local version with my advice_fn, wont work with official version

main.dir = here::here()

```

# Code modified from the SPASM.MSE vignettes 

Vignettes found [here](https://lichengxue.github.io/SPASAM.MSE/index.html)

Starting point is this one https://lichengxue.github.io/SPASAM.MSE/Use-Actual-Stock-Assessment.html 

And modifying to test the addition of the MAFMC risk policy and ABC HCR that I added to my own version of  `SPASAM.MSE::advice_fn()`

## Operating model setup

### Basic information

This is all modified for butterfish

The 2022 butterfish RT models are posted online in the SASI portal [here](https://apps-nefsc.fisheries.noaa.gov/saw/sasi_files.php?year=2022&species_id=16&stock_id=6&review_type_id=5&info_type_id=3&map_type_id=&filename=WHAM_models.zip). 

MT assessments are not posted (maybe someday?) but Chuck kindly sent the 2024 MT outputs when I requested them; and converted them to multi-wham, which I think made all the difference. A day or two was spent trying to make the RT model work but it kept blowing up because WHAM 2.0 is very different from WHAM 1.0

Read in the models (2024 MT in WHAM 2.0)

```{r}
# buttermods <- readRDS(here::here("./assessments/Butterfish2022_WHAM_models/mods.rds"))
# 
# buttermods[[1]]$model_name
# buttermods[[2]]$model_name
# buttermods[[3]]$model_name
# 
# base2022 <- buttermods[[1]] # ASAP in WHAM
# recdev2022 <- buttermods[[2]] # This with only rec RE may be closer to the example from the vignette
# NAAmod2022 <- buttermods[[3]] # This is the preferred model with NAA RE

buttermod <- readRDS(here::here("./assessments/Butterfish2022_WHAM_models/naa5_2024MT_multiwham.rds"))

buttermod$wham_version
```

Can I use these as a basis? Follow https://lichengxue.github.io/SPASAM.MSE/Use-Actual-Stock-Assessment.html 

Need to figure out how to read in only the inputs, may be possible using code in https://timjmiller.github.io/wham/articles/ex13_no_ASAP.html

Global settings

```{r}

input_hist <- buttermod$input #prepare_wham_input(gb_dat)
input      <- buttermod$input #prepare_wham_input(gb_dat)

n_stocks  <- 1L
n_regions <- 1L
n_ages    <- 5L # NAAmod2022$input$data$n_ages is 5
n_indices <- 6L # NAAmod2022$input$data$n_indices is 6
n_fleets  <- 1L # NAAmod2022$input$data$n_fleets is 1
n_seasons <- 1L

# butterfish RT assessment start and end data years NAAmod2022$years, updated for 2024 MT
year_start  <- 1989L
year_end    <- 2023L
MSE_years   <- 9L # 3 3yr assessment cycles

n_hist_years <- year_end - year_start + 1L
n_proj_years <- n_hist_years + MSE_years

base_years      <- year_start:year_end
assess_interval <- 3L

stopifnot(MSE_years %% assess_interval == 0L)

assess_years <- seq(
  tail(base_years, 1),
  year_end + MSE_years - assess_interval,
  by = assess_interval
)

# Historical period is fixed.
# Only years from first_free_year onward are allowed to vary.
first_free_year <- 36L # year after last historical year

```

Historical model

I don't need most of this because I want to use the original assessment directly. Kept the code blocks but mostly commented out below aside from variables used later

Bio inputs

```{r}
# user_maturity_hist <- array(NA_real_, dim = c(n_stocks, n_hist_years, n_ages))
# user_maturity_hist[, 1:n_hist_years, ] <- input$data$mature
# 
# user_waa_hist <- list()
# user_waa_hist$waa <- array(NA_real_, dim = c(2, n_hist_years, n_ages))
# user_waa_hist$waa[, 1:n_hist_years, ] <- input$data$waa
# user_waa_hist$waa_pointer_fleets   <- input$data$waa_pointer_fleets
# user_waa_hist$waa_pointer_indices  <- input$data$waa_pointer_indices[-1] #there are 6 indices and 7 here?
# user_waa_hist$waa_pointer_totcatch <- input$data$waa_pointer_totcatch
# user_waa_hist$waa_pointer_ssb      <- input$data$waa_pointer_ssb
# user_waa_hist$waa_pointer_M        <- input$data$waa_pointer_M

fracyr_spawn <- input$asap3[[1]]$fracyr_spawn #gb_dat[[1]]$dat$fracyr_spawn
```

Catch and index observation settings

```{r}
# catch_info_hist <- list(
#   catch_cv      = 0.3,
#   catch_Neff    = 41,
#   use_agg_catch = 1,
#   use_catch_paa = 1
# )
# 
# index_info_hist <- list(
#   index_cv        = c(0.4699923, 0.5389348, 0.6166915, 0.5313571, 0.7573711, 0.3517145), #rep(0.5, n_indices),
#   index_Neff      = c(10.967742,  4.838710,  1.677419,  4.967742,  1.064516, 0.000000), #rep(25, n_indices),
#   fracyr_indices  = c(0.75, 0.75, 0.75, 0.25, 0.3333333, 0.75),
#   q               = rep(0.2, n_indices),
#   use_indices     = rep(1, n_indices),
#   use_index_paa   = rep(1, n_indices),
#   units_indices   = rep(2, n_indices),
#   units_index_paa = rep(2, n_indices)
# )
```

Alternatively take from the assessment? Try if not using the full fitted assessment, not necessary here

```{r}

# from  https://timjmiller.github.io/wham/articles/ex13_no_ASAP.html

# basic_info_hist <- list(
#     n_stocks = 1L,
#     n_seasons = 1L,
#     n_fleets = 1L,
#     ages = 1:input$data$n_ages,
#     n_fleets = input$data$n_fleets,
#     fracyr_SSB = cbind(input$data$fracyr_SSB), #(n_years x n_stocks)
#     maturity = input$data$mature, #(n_stocks x n_years x n_ages)
#     years = as.integer(input$years), #(n_years)
#     waa = input$data$waa, #(any no. x n_years x n_ages)
#     waa_pointer_ssb = input$data$waa_pointer_ssb, #(n_stocks)
#     spawn_regions = 1, #(n_stocks)
#     spawn_seasons = 1 #(n_stocks)
# )
# 
# catch_info_hist <- list(
#     n_fleets = NCOL(input$data$agg_catch), #(n_fleets)
#     agg_catch = cbind(input$data$agg_catch), #(n_years x n_fleets)
#     agg_catch_cv = cbind(sqrt(exp(input$data$agg_catch_sigma^2) - 1)), #(n_years x n_fleets)
#     catch_paa = input$data$catch_paa, #(n_fleets x n_years x n_ages)
#     use_catch_paa = cbind(input$data$use_catch_paa), #(n_years x n_fleets), 0: don't use, 1: use
#     catch_Neff = cbind(input$data$catch_Neff), #(n_years x n_fleets)
#     selblock_pointer_fleets = cbind(input$data$selblock_pointer_fleets), #(n_years x n_fleets)
#     waa_pointer_fleets = input$data$waa_pointer_fleets, #(n_fleets)
#     fleet_regions = rep(1,input$data$n_fleets) #(n_fleets)
# )
# 
# index_info_hist <- list(
#     n_indices = NCOL(input$data$agg_indices),
#     agg_indices = cbind(input$data$agg_indices), #(n_years x n_indices)
#     units_indices = input$data$units_indices, #(n_indices) 1: biomass 2: numbers
#     units_index_paa = input$data$units_index_paa, #(n_indices) 1: biomass 2: numbers
#     agg_index_cv = cbind(sqrt(exp(input$data$agg_index_sigma^2) - 1)), #(n_years x n_indices)
#     index_Neff = cbind(input$data$index_Neff), #(n_years x n_indices)
#     fracyr_indices = cbind(input$data$fracyr_indices), #(n_years x n_indices)
#     use_indices = cbind(input$data$use_indices), #(n_years x n_indices)
#     use_index_paa = cbind(input$data$use_index_paa),  #(n_years x n_indices)
#     index_paa = input$data$index_paa,  #(n_indices x n_years x n_ages)
#     selblock_pointer_indices = cbind(input$data$selblock_pointer_indices), #(n_years x n_indices)
#     waa_pointer_indices = input$data$waa_pointer_indices, #(n_indices)
#     index_regions = rep(1,input$data$n_indices) #(n_indices)
# ) 



```

Build the model scaffold

```{r}
# info_hist <- SPASAM.MSE::generate_basic_info(
#   n_stocks = n_stocks,
#   n_regions = n_regions,
#   n_indices = n_indices,
#   n_fleets = n_fleets,
#   n_seasons = n_seasons,
#   base.years = year_start:year_end,
#   n_feedback_years = 0L,
#   n_ages = n_ages,
#   catch_info = catch_info_hist,
#   index_info = index_info_hist,
#   user_waa = user_waa_hist,
#   user_maturity = user_maturity_hist,
#   fracyr_spawn = fracyr_spawn,
#   life_history = "short"
# )
# 
# #basic_info_hist     <- info_hist$basic_info
# catch_info_use_hist <- info_hist$catch_info
# index_info_use_hist <- info_hist$index_info
# F_info_hist         <- info_hist$F
# 
# catch_info_use_hist$agg_catch[1:n_hist_years, ]     <- input$data$agg_catch
# catch_info_use_hist$catch_paa[, 1:n_hist_years, ]   <- input$data$catch_paa
# index_info_use_hist$agg_indices[1:n_hist_years, ]   <- input$data$agg_indices
# index_info_use_hist$index_paa[, 1:n_hist_years, ]   <- input$data$index_paa
# index_info_use_hist$use_indices[1:n_hist_years, ]   <- input$data$use_indices
# index_info_use_hist$use_index_paa[1:n_hist_years, ] <- input$data$use_index_paa
```

Selectivity, M, etc

I started redimensioning this but stopped because I'm just reading in the original butterfish model

```{r}
# sel_hist <- list(
#   model = c("age-specific", "logistic", "logistic", "logistic", "logistic", "logistic", "logistic"),
#   re    = c("ar1_y", "none", "none", "none", "none", "none", "none"),
#   initial_pars = list(
#     c(0.1, 0.25, 0.5, 1, 1),
#     c(2, 0.3),
#     c(2, 0.3),
#     c(2, 0.3),
#     c(2, 0.3),
#     c(2, 0.3),
#     c(2, 0.3)
# 
#   ),
#   fix_pars = list(c(4:6), NULL, NULL, NULL, NULL, NULL, NULL)
# )
# 
# M_hist <- list(
#   model = "constant",
#   initial_means = array(
#     c(0.57, 0.33, 0.26, 0.23, 0.22),
#     dim = c(n_stocks, n_regions, n_ages)
#   )
# )
# 
# sigma_vals_hist <- array(0, dim = c(n_stocks, n_regions, n_ages))
# sigma_vals_hist[, , 1] <- 0.5
# 
# NAA_re_hist <- list(
#   N1_model      = rep("equilibrium", n_stocks),
#   sigma         = rep("rec", n_stocks),
#   cor           = rep("iid", n_stocks),
#   recruit_model = 2,
#   sigma_vals    = sigma_vals_hist
# )
```

Prep and fit historical model, not doing this just reading in 2024 MT model in WHAM 2.0

```{r}
# input_histfit <- prepare_wham_input(
#   basic_info  = basic_info_hist,
#   selectivity = sel_hist,
#   M           = M_hist,
#   NAA_re      = NAA_re_hist,
#   catch_info  = catch_info_use_hist,
#   index_info  = index_info_use_hist,
#   F           = F_info_hist,
#   age_comp    = "logistic-normal-pool0"
# )
# 
# input_histfit <- update_waa(input_histfit, waa_info = info_hist$par_inputs$user_waa)
# 
# input_e <- input #prepare_wham_input(gb_dat)
# input_histfit$data$agg_index_sigma[1:n_hist_years, ] <- input_e$data$agg_index_sigma
# input_histfit$data$use_indices[1:n_hist_years, ]     <- input_e$data$use_indices
# input_histfit$data$use_index_paa[1:n_hist_years, ]   <- input_e$data$use_index_paa
# 
# generate_remove_years <- function(mat) {
#   lz <- lapply(seq_len(ncol(mat)), function(j) which(mat[, j] == 0))
#   if (all(lengths(lz) == 0)) return(NULL)
#   max_rows <- max(sapply(lz, length))
#   out <- matrix(NA_integer_, nrow = max_rows, ncol = length(lz))
#   for (j in seq_along(lz)) {
#     if (length(lz[[j]])) out[seq_along(lz[[j]]), j] <- lz[[j]]
#   }
#   out
# }
# 
# remove_agg_years1 <- generate_remove_years(input_e$data$use_indices)
# remove_paa_years1 <- generate_remove_years(input_e$data$use_index_paa)
# 
# input_histfit <- update_input_index_info(
#   input_histfit,
#   agg_index_sigma = input_histfit$data$agg_index_sigma,
#   index_Neff      = input_histfit$data$index_Neff,
#   remove_agg = TRUE,
#   remove_agg_pointer = 1:3,
#   remove_agg_years = remove_agg_years1,
#   remove_paa = TRUE,
#   remove_paa_pointer = 1:3,
#   remove_paa_years = remove_paa_years1
# )

# om_file <- system.file("extdata", "OM.RDS", package = "SPASAM.MSE")
# 
# if (file.exists(om_file)) {
#   
#   OM <- readRDS(om_file)
#   
# } else {
#   
#.  # This blows up every time
  # OM <- fit_wham(
  #   input_histfit,
  #   do.fit = TRUE,
  #   do.brps = TRUE,
  #   do.retro = FALSE,
  #   do.osa = FALSE,
  #   MakeADFun.silent = TRUE
  # )
#   
#   saveRDS(OM, file.path(tempdir(), "OM.RDS"))
#   
# }

# could the initial OM not be the fitted model?

OM <- buttermod

check_convergence(OM)
```


### Extend assessment to do free projections

Now try using the original model as is and extending to projections. Go back to Cheng's code (adjusted some dims here (waa from 5 in the example to 8))

```{r}
user_maturity <- array(NA_real_, dim = c(n_stocks, n_proj_years, n_ages))
user_maturity[, 1:n_hist_years, ] <- OM$input$data$mature[, 1:n_hist_years, ]
for (iy in (n_hist_years + 1L):n_proj_years) {
  user_maturity[, iy, ] <- OM$input$data$mature[, n_hist_years, , drop = FALSE]
}

user_waa <- list()
user_waa$waa <- array(NA_real_, dim = c(8, n_proj_years, n_ages))
user_waa$waa[, 1:n_hist_years, ] <- OM$input$data$waa[, 1:n_hist_years, ]
for (iy in (n_hist_years + 1L):n_proj_years) {
  user_waa$waa[, iy, ] <- OM$input$data$waa[, n_hist_years, , drop = FALSE]
}

user_waa$waa_pointer_fleets   <- OM$input$data$waa_pointer_fleets
user_waa$waa_pointer_indices  <- OM$input$data$waa_pointer_indices
user_waa$waa_pointer_totcatch <- OM$input$data$waa_pointer_totcatch
user_waa$waa_pointer_ssb      <- OM$input$data$waa_pointer_ssb
user_waa$waa_pointer_M        <- OM$input$data$waa_pointer_M # this is null in input but gets set equal to waa_pointer_ssb anyway
# all of these get overwritten anyway, hardcoded in SPASAM.MSE::generate_basic_info

```

Catch and index

```{r}
# catch_info <- list(
#   catch_cv      = 0.05,
#   catch_Neff    = 50,
#   use_agg_catch = 1,
#   use_catch_paa = 1
# )
# 
# index_info <- list(
#   index_cv        = rep(0.5, n_indices),
#   index_Neff      = rep(25, n_indices),
#   fracyr_indices  = c(0.25, 0.75, 0.25),
#   q               = c(2.110e-4, 2.247e-4, 2.683e-4),
#   use_indices     = rep(1, n_indices),
#   use_index_paa   = rep(1, n_indices),
#   units_indices   = rep(2, n_indices),
#   units_index_paa = rep(2, n_indices)
# )

catch_info <- list(
  catch_cv      = 0.2623537, #mean(input$data$agg_catch_sigma)
  catch_Neff    = 43, #input$data$catch_Neff
  use_agg_catch = 1,
  use_catch_paa = 1
)

index_info <- list(
  index_cv        = c(0.5010909, 0.5451420, 0.5038754, 0.5337914, 0.6915221, 0.3634754), #rep(0.5, n_indices), colMeans(input$data$agg_index_sigma)
  index_Neff      = c(20,  17,  5,  24,  3, 0), #rep(25, n_indices), took constants for each index in input$data$index_Neff
  fracyr_indices  = c(0.75, 0.75, 0.75, 0.25, 0.3333333, 0.75), #input$data$fracyr_indices
  q               = c(0.197517, 0.523248, 0.1647172, 0.464651, 0.1039347, 3.424289e-05), #rep(0.2, n_indices), OM$rep$q
  use_indices     = rep(1, n_indices),
  use_index_paa   = c(rep(1, n_indices-1), 0),
  units_indices   = rep(2, n_indices),
  units_index_paa = rep(2, n_indices)
)
```

Scaffold

```{r}
info <- SPASAM.MSE::generate_basic_info(
  n_stocks = n_stocks,
  n_regions = n_regions,
  n_indices = n_indices,
  n_fleets = n_fleets,
  n_seasons = n_seasons,
  base.years = year_start:year_end,
  n_feedback_years = MSE_years,
  n_ages = n_ages,
  #life_history = "short", #added; need?
  catch_info = catch_info,
  index_info = index_info,
  user_waa = user_waa,
  user_maturity = user_maturity,
  fracyr_spawn = fracyr_spawn
)

basic_info     <- info$basic_info
catch_info_use <- info$catch_info
index_info_use <- info$index_info

#catch_info_use$selblock_pointer_fleets[1:n_hist_years, ] <- input$data$selblock_pointer_fleets

catch_info_use$agg_catch[1:n_hist_years, ]     <- input$data$agg_catch
catch_info_use$catch_paa[, 1:n_hist_years, ]   <- input$data$catch_paa

index_info_use$agg_indices[1:n_hist_years, ]   <- input$data$agg_indices
index_info_use$index_paa[, 1:n_hist_years, ]   <- input$data$index_paa
#index_info_use$use_indices[1:n_hist_years, ]   <- input$data$use_indices #added later
#index_info_use$use_index_paa[1:n_hist_years, ] <- input$data$use_index_paa #added later

```

Initialize F

```{r}
F_info <- info$F
F_info$F[1:n_hist_years, ] <- OM$rep$Fbar[1:n_hist_years, drop = FALSE]
```

Selectivity, M, and process in OM

```{r}
sel3 <- list(
  n_selblocks = OM$input$data$n_selblocks, # added
  model = rep("age-specific", 8), #input$data$selblock_models = 1 for all
  re    = rep("none", 8), #input$data$selblock_models_re = 1 for all
  initial_pars = list( #from OM$rep$selAA
    c(0.013508, 0.1829535, 0.642894,    1, 0.532285),
    c(0.003615705, 0.06812128, 0.3757382,    1, 0.5632194),
    c(1, 0.5265157, 0.4638104, 0.102919, 0.05952474),
    c(1, 0.6590912, 0.7439251, 0.4416134, 0.09534809),
    c(1,    1, 0.0836746, 0.05080942, 0.06792671),
    c(0,    1, 0.4274524, 0.5378442, 0.2198267),
    c(0.0221619,    1,    1, 0.07488138, 0.3999979),
    c(1,    0,    0,    0,   0)
  ),
  fix_pars = list(4, 4, 1, 1, 1:2, 1:2, 2, 1:5) # fix at least one at 1 for age specific
)

# OM$input$data$selblock_pointer_fleets has selectivity years for fishery, added

M <- list(
  model = "constant",
  initial_means = array(
    c(1.278, 1.278, 1.278, 1.278, 1.278),
    dim = c(n_stocks, n_regions, n_ages)
  )
)

sigma_vals <- array(0, dim = c(n_stocks, n_regions, n_ages))
sigma_vals[, , 1] <- exp(OM$parList$log_NAA_sigma[, , 1])
sigma_vals[, , 2:n_ages] <- exp(OM$parList$log_NAA_sigma[, , 2:n_ages])

recruit_pars_use <- exp(as.numeric(OM$parList$mean_rec_pars[1, ]))

NAA_re <- list(
  N1_model      = rep("age-specific-fe", n_stocks),
  sigma         = rep("rec+1", n_stocks),
  cor           = rep("iid", n_stocks),
  recruit_model = 2,
  recruit_pars  = list(recruit_pars_use),
  sigma_vals    = sigma_vals
)
```

Now trying to make the OM


```{r}

# will this fix error?
# basic_info$waa_pointer_ssb <- NULL
# basic_info$waa_pointer_M <- NULL

om_input_P <- wham::prepare_wham_input(
  basic_info  = basic_info,
  selectivity = sel3,
  M           = M,
  NAA_re      = NAA_re,
  catch_info  = catch_info_use,
  index_info  = index_info_use,
  F           = F_info,
  age_comp    = "multinomial"
)

waa_info <- info$par_inputs$user_waa
om_input_P <- SPASAM.MSE::update_waa(om_input_P, waa_info = waa_info)

om_input_P$par$catch_paa_pars <- OM$parList$catch_paa_pars #<- matrix(0, basic_info$n_fleets, 3) #these were not in the old OM
om_input_P$par$index_paa_pars <- OM$parList$index_paa_pars #<- matrix(0, basic_info$n_indices, 3) #these were not in the old OM
om_input_P$par$sel_repars     <- OM$parList$sel_repars

for (i in 1:n_regions) {
  om_input_P$par$log_N1[i, i, ] <- log(OM$rep$N1)[i, i, ] #log(OM$rep$NAA[i, 1])  #for old model
}

om_input_P$data$agg_catch_sigma[1:n_hist_years, ] <- input_hist$data$agg_catch_sigma
om_input_P$data$selblock_pointer_fleets[1:n_hist_years, ] <- input_hist$data$selblock_pointer_fleets

om_input_P$data$agg_index_sigma[1:n_hist_years, ] <- input_hist$data$agg_index_sigma
om_input_P$data$use_indices[1:n_hist_years, ]     <- input_hist$data$use_indices
om_input_P$data$use_index_paa[1:n_hist_years, ]   <- input_hist$data$use_index_paa

for (iy in (n_hist_years + 1L):n_proj_years) {
  om_input_P$data$agg_index_sigma[iy, ] <- input_hist$data$agg_index_sigma[n_hist_years, ]
  om_input_P$data$agg_catch_sigma[iy, ] <- input_hist$data$agg_catch_sigma[n_hist_years, ]
  om_input_P$data$selblock_pointer_fleets [iy, ] <- input_hist$data$selblock_pointer_fleets[n_hist_years, ]
}
```

Now adding back indices with years to use, works now

```{r}
loc_zeros_agg <- lapply(seq_len(ncol(input_hist$data$use_indices)), function(j) {
  which(input_hist$data$use_indices[, j] == 0)
})

loc_zeros_paa <- lapply(seq_len(ncol(input_hist$data$use_index_paa)), function(j) {
  which(input_hist$data$use_index_paa[, j] == 0)
})

max_agg <- max(sapply(loc_zeros_agg, length))
max_paa <- max(sapply(loc_zeros_paa, length))

remove_agg_years1 <- if (max_agg > 0) {
  out <- matrix(NA_integer_, nrow = max_agg, ncol = length(loc_zeros_agg))
  for (j in seq_along(loc_zeros_agg)) {
    if (length(loc_zeros_agg[[j]])) {
      out[seq_along(loc_zeros_agg[[j]]), j] <- loc_zeros_agg[[j]]
    }
  }
  out
} else NULL

remove_paa_years1 <- if (max_paa > 0) {
  out <- matrix(NA_integer_, nrow = max_paa, ncol = length(loc_zeros_paa))
  for (j in seq_along(loc_zeros_paa)) {
    if (length(loc_zeros_paa[[j]])) {
      out[seq_along(loc_zeros_paa[[j]]), j] <- loc_zeros_paa[[j]]
    }
  }
  out
} else NULL

om_input_P <- SPASAM.MSE::update_input_index_info(
  om_input_P,
  agg_index_sigma = om_input_P$data$agg_index_sigma,
  index_Neff      = om_input_P$data$index_Neff,
  remove_agg = TRUE,
  remove_agg_pointer = 1:6,
  remove_agg_years = remove_agg_years1,
  remove_paa = TRUE,
  remove_paa_pointer = 1:6,
  remove_paa_years = remove_paa_years1
)
```

Now compile projection OM, fingers crossed--works, it was all the old WHAM format causing issues

```{r}
om_input_P$data$do_simulate_N_re <- 1L

unfitted_om_P <- fit_wham(
  om_input_P,
  do.fit = FALSE,
  do.brps = FALSE,
  MakeADFun.silent = TRUE
)
```

Fix history, free future

```{r}
unfitted_om_P$input$random <- "log_NAA"
unfitted_om_P$input$data$do_simulate_N_re <- 1L

unfitted_om_P$input$par$log_N1 <- log(OM$rep$N1)
if (!is.null(unfitted_om_P$parList$log_N1)) {
  unfitted_om_P$parList$log_N1 <- log(OM$rep$N1)
}

hist_idx <- 1:(first_free_year - 2L) 
unfitted_om_P$input$par$log_NAA[1, 1, hist_idx, ] <-
  log(OM$rep$NAA[1, 1, hist_idx + 1L, ])

if (!is.null(unfitted_om_P$parList$log_NAA)) {
  unfitted_om_P$parList$log_NAA[1, 1, hist_idx, ] <-
    log(OM$rep$NAA[1, 1, hist_idx + 1L, ])
}
```

```{r}
logNAA_dim <- dim(unfitted_om_P$input$par$log_NAA)
future_idx_start <- first_free_year - 1L
future_idx <- future_idx_start:logNAA_dim[3]

m <- array(NA_integer_, dim = logNAA_dim)
m[1, 1, future_idx, ] <- 1L
m[!is.na(m)] <- seq_len(sum(!is.na(m)))

unfitted_om_P$input$map$log_NAA <- factor(m)
if (!is.null(unfitted_om_P$env$map)) {
  unfitted_om_P$env$map$log_NAA <- unfitted_om_P$input$map$log_NAA
}
```

```{r}
last_fixed_idx <- first_free_year - 2L
if (last_fixed_idx >= 1L) {
  unfitted_om_P$input$par$log_NAA[1, 1, future_idx, ] <-
    array(
      unfitted_om_P$input$par$log_NAA[1, 1, last_fixed_idx, ],
      dim = c(1, 1, length(future_idx), logNAA_dim[4])
    )

  if (!is.null(unfitted_om_P$parList$log_NAA)) {
    unfitted_om_P$parList$log_NAA[1, 1, future_idx, ] <-
      array(
        unfitted_om_P$parList$log_NAA[1, 1, last_fixed_idx, ],
        dim = c(1, 1, length(future_idx), logNAA_dim[4])
      )
  }
}

unfitted_om_P$parList$logit_selpars <- OM$parList$logit_selpars
unfitted_om_P$parList$selpars_re    <- OM$parList$selpars_re
```

```{r}
unfitted_om_P <- fit_wham(
  unfitted_om_P$input,
  do.fit = FALSE,
  do.brps = FALSE,
  MakeADFun.silent = TRUE
)
```

Simulate the future

```{r}
seed <- 12345L

om_future <- update_om_fn(
  unfitted_om_P,
  seed = seed,
  random = "log_NAA",
  process_fix = TRUE,
  first_free_year = first_free_year
)
```

### Check OM with free projection

Check for fixed history: works!

SSB

```{r}
plot(
  om_future$rep$SSB,
  type = "l",
  main = "SSB with fixed history and simulated feedback period",
  xlab = "Model year",
  ylab = "SSB"
)
lines(1:n_hist_years, OM$rep$SSB[1:n_hist_years], col = "red", lwd = 2)

legend(
  "topright",
  legend = c("Projected OM", "Fitted historical OM"),
  col = c("black", "red"),
  lwd = c(1, 2),
  bty = "n"
)
```

NAA comparisons (modified from original age 6, too old for butterfish, set to 3)

```{r}
s <- 1
r <- 1
hist_idx <- 1:(n_hist_years - 1L)

layout(matrix(c(1,2,3), nrow = 3, byrow = TRUE))
par(mar = c(4,4,2,1))

# Extract series
input_series <- exp(om_future$input$par$log_NAA[s, r, hist_idx, 1])
fitted_series <- OM$rep$NAA[s, r, hist_idx + 1L, 1]

# Panel 1 — overlay
plot(hist_idx + 1, input_series,
     type = "l",
     lwd = 2,
     xlab = "Model year",
     ylab = "NAA age 1",
     main = "Input vs Fitted (age 1)")
lines(hist_idx + 1, fitted_series, col = "red", lwd = 2)
legend("topright", c("Input", "Fitted"), col=c("black","red"), lty=1)

# Panel 2 — difference
plot(hist_idx + 1,
     input_series - fitted_series,
     type = "l",
     xlab = "Model year",
     ylab = "Difference",
     main = "Input − Fitted")
abline(h = 0, lty = 2)

# Panel 3 — predicted NAA age 3
plot(
  om_future$rep$pred_NAA[s, r, , 3],
  type = "l",
  main = "Predicted Number at Age 3",
  xlab = "Model year",
  ylab = "Predicted NAA age 3"
)
abline(v = first_free_year, lty = 2, col = "red")
```

Rec devs

```{r}
par(mfrow = c(2, 1))

# Recruitment deviations
matplot(
  om_future$rep$NAA_devs[, , , 1],
  type = "l",
  lty = 1,
  col = rainbow(dim(om_future$rep$NAA_devs)[1]),
  main = "Log Recruitment Deviations",
  xlab = "Year",
  ylab = "Value"
)

# Predicted recruitment
matplot(
  om_future$rep$pred_NAA[, , , 1],
  type = "l",
  lty = 1,
  col = rainbow(dim(om_future$rep$pred_NAA)[1]),
  main = "Predicted Recruitment",
  xlab = "Year",
  ylab = "Value"
)

par(mfrow = c(1,1))
```

Historical SSB is identical because I did not refit the model, just used 2024 MT as is. 

```{r}
hist_diff <- om_future$rep$NAA[, , 1:n_hist_years, ] -
  OM$rep$NAA[, , 1:n_hist_years, ]
print(hist_diff)

plot(
  om_future$rep$SSB[1:n_hist_years],
  type = "l",
  main = "Historical SSB comparison",
  xlab = "Year index",
  ylab = "SSB"
)
lines(OM$rep$SSB[1:n_hist_years], col = "red")
```

OK but catch history? Predicted catch is the same

```{r}
plot(
  om_future$rep$pred_catch, #[1:n_hist_years],
  type = "l",
  main = "Historical Catch comparison",
  xlab = "Year index",
  ylab = "Pred Catch"
)
lines(OM$rep$pred_catch, col = "red")
```

Input catch is different, should I be worried? Input catch appears to go to the EM so maybe yes

```{r}
plot(
  om_future$input$data$agg_catch, #[1:n_hist_years],
  type = "l",
  main = "Input Catch comparison",
  xlab = "Year index",
  ylab = "Input Catch"
)
lines(OM$input$data$agg_catch, col = "red")
```


### Now try an MSE

Assessment years and settings for EM, at first change only assessment interval to 3

```{r}
assess_interval <- 3L
base_years      <- year_start:year_end
terminal_year   <- tail(base_years, 1)

assess_years <- seq(
  terminal_year,
  year_end + MSE_years - assess_interval,
  by = assess_interval
)

NAA_re_em <- NAA_re
NAA_re_em$N1_model <- "equilibrium"
NAA_re_em$sigma    <- "rec"
NAA_re_em$cor      <- "iid"

update_catch_info_list <- list(
  agg_catch_sigma = om_input_P$data$agg_catch_sigma,
  catch_Neff      = om_input_P$data$catch_Neff
)

update_index_info_list <- list(
  agg_index_sigma = om_input_P$data$agg_index_sigma,
  index_Neff      = om_input_P$data$index_Neff,
  remove_agg = TRUE,
  remove_agg_pointer = 1:6,
  remove_agg_years = remove_agg_years1,
  remove_paa = TRUE,
  remove_paa_pointer = 1:6,
  remove_paa_years = remove_paa_years1
)

#info$catch_info$selblock_pointer_fleets  <-  OM$input$data$selblock_pointer_fleets #added


```

HCR Type 1, 75% FXSPR

Some issues:

*  The fleet selectivity block pointer is not getting passed to the EM even when I add it directly to the info object above

*  EM Input catch as noted above is different from the OM rep catch (same as original catch) and matches the OM input catch

*  The EM is not converging. Catch in the first year is astronomical trying to use the reference point so my first try is subbing in the SSC F ref pt of 2/3M

*  Also the EM is nothing like the actual assessment... 


```{r}
hcr1 <- list(
  hcr.type = 1,
  hcr.opts = list(use_FXSPR = TRUE, percentFXSPR = 75)
)

# mod1_file <- system.file("extdata", "mod1.RDS", package = "SPASAM.MSE")
# 
# if (file.exists(mod1_file)) {
#   
#   mod1 <- readRDS(mod1_file)
#   
# } else {
  
  mod1 <- loop_through_fn(
    om = om_future,
    em_info = info,
    random = "log_NAA",
    M_em = M,
    sel_em = sel3,
    NAA_re_em = NAA_re_em,
    age_comp_em = "logistic-normal-pool0",
    em.opt = list(
      separate.em = FALSE,
      separate.em.type = 1,
      do.move = FALSE,
      est.move = FALSE
    ),
    update_index_info = update_index_info_list,
    update_catch_info = update_catch_info_list,
    assess_years = assess_years,
    assess_interval = assess_interval,
    base_years = base_years,
    year.use = 35,
    add.years = TRUE,
    seed = 12345L,
    hcr = hcr1,
    save.sdrep = FALSE,
    save.last.em = TRUE,
    FXSPR_init = 0.5,
    process_fix = TRUE,
    first_free_year = 36
  )
  
#}
```

HCR Type 1, 100% FXSPR

```{r}
hcr2 <- list(
  hcr.type = 1,
  hcr.opts = list(use_FXSPR = TRUE, percentFXSPR = 100)
)

# mod2_file <- system.file("extdata", "mod2.RDS", package = "SPASAM.MSE")
# 
# if (file.exists(mod2_file)) {
#   
#   mod2 <- readRDS(mod2_file)
#   
# } else {
  
  mod2 <- loop_through_fn(
    om = om_future,
    em_info = info,
    random = "log_NAA",
    M_em = M,
    sel_em = sel3,
    NAA_re_em = NAA_re_em,
    age_comp_em = "logistic-normal-pool0",
    em.opt = list(
      separate.em = FALSE,
      separate.em.type = 1,
      do.move = FALSE,
      est.move = FALSE
    ),
    update_index_info = update_index_info_list,
    update_catch_info = update_catch_info_list,
    assess_years = assess_years,
    assess_interval = assess_interval,
    base_years = base_years,
    year.use = 35,
    add.years = TRUE,
    seed = 12345L,
    hcr = hcr2,
    save.sdrep = FALSE,
    save.last.em = TRUE,
    FXSPR_init = 0.5,
    process_fix = TRUE,
    first_free_year = 36
  )
  
#}
```

Now try the MAFMC rule, HCR type 4

```{r}
hcr3 <- list(
  hcr.type = 4,
  hcr.opts = list(use_FXSPR = TRUE)
)

# mod2_file <- system.file("extdata", "mod2.RDS", package = "SPASAM.MSE")
# 
# if (file.exists(mod2_file)) {
#   
#   mod2 <- readRDS(mod2_file)
#   
# } else {
  
  mod3 <- loop_through_fn(
    om = om_future,
    em_info = info,
    random = "log_NAA",
    M_em = M,
    sel_em = sel3,
    NAA_re_em = NAA_re_em,
    age_comp_em = "logistic-normal-pool0",
    em.opt = list(
      separate.em = FALSE,
      separate.em.type = 1,
      do.move = FALSE,
      est.move = FALSE
    ),
    update_index_info = update_index_info_list,
    update_catch_info = update_catch_info_list,
    assess_years = assess_years,
    assess_interval = assess_interval,
    base_years = base_years,
    year.use = 35,
    add.years = TRUE,
    seed = 12345L,
    hcr = hcr3,
    save.sdrep = FALSE,
    save.last.em = TRUE,
    FXSPR_init = 0.5,
    process_fix = TRUE,
    first_free_year = 36
  )
  
```

Compare HCRs

```{r}
plot(
  mod1$om$rep$SSB,
  type = "l",
  lwd = 2,
  col = "blue",
  xlab = "Year index",
  ylab = "SSB",
  main = "MSE comparison: SSB under three HCR settings"
)

lines(
  mod2$om$rep$SSB,
  col = "red",
  lwd = 2,
  lty = 2
)

lines(
  mod3$om$rep$SSB,
  col = "green",
  lwd = 2,
  lty = 2
)

abline(v = first_free_year, lty = 3)

legend(
  "topright",
  legend = c("75% FXSPR", "100% FXSPR", "Mid HCR", "Start of feedback period"),
  col = c("blue", "red", "green", "black"),
  lty = c(1, 2, 3, 4),
  lwd = c(2, 2, 2, 1),
  bty = "n"
)
```

I probably need to change some numbers because the start of the feedback period should be right after the assessment? Or include assessment projections?


## Simpler not from assessment

To be added