---
title: "Test Harvest Control Rule"
author: "Sarah Gaichas"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(wham)
library(SPASAM.MSE)

main.dir = here::here()

```

# Code taken from the SPASM.MSE vignettes [here](https://lichengxue.github.io/SPASAM.MSE/index.html)

Starting with this one https://lichengxue.github.io/SPASAM.MSE/Harvest-Control-Rule.html

And modifying to test the addition of the MAFMC risk policy and ABC HCR to  `SPASAM.MSE::advice_fn()`

First run the code as is

## Operating model setup

### Basic information

```{r}
year_start  <- 1
year_end    <- 20
MSE_years   <- 3

info <- generate_basic_info(
  n_stocks = 2,
  n_regions = 2,
  n_indices = 2,
  n_fleets = 2,
  n_seasons = 1,
  base.years = year_start:year_end,
  n_feedback_years = MSE_years,
  life_history = "medium",
  n_ages = 12
)

basic_info = info$basic_info
catch_info = info$catch_info
index_info = info$index_info
F_info     = info$F
```

### Specify movement

```{r}
basic_info <- generate_NAA_where(basic_info, move.type = 2)
move <- generate_move(
  basic_info = basic_info,
  move.type = 2,
  move.rate = c(0.3, 0.1),
  move.re = "constant"
)
```

### Configure selectivity

```{r}
n_stocks  <- as.integer(basic_info['n_stocks'])
n_regions <- as.integer(basic_info['n_regions'])
n_fleets  <- as.integer(basic_info['n_fleets'])
n_indices <- as.integer(basic_info['n_indices'])
n_ages    <- as.integer(basic_info['n_ages'])

fleet_pars <- c(5, 1)
index_pars <- c(2, 1)
sel <- list(
  model = rep("logistic", n_fleets + n_indices),
  initial_pars = c(rep(list(fleet_pars), n_fleets), rep(list(index_pars), n_indices))
)
```

### Configure NAA

```{r}
sigma      <- "rec+1"
re_cor     <- "iid"
ini.opt    <- "equilibrium"
Rec_sig    <- 0.5
NAA_sig    <- 0.2

sigma_vals <- array(NAA_sig, dim = c(n_stocks, n_regions, n_ages))
sigma_vals[,,1] <- Rec_sig

log_N1    <- rep(10, n_stocks)
log_N1[1] <- log(exp(10) * 2)
N1_pars   <- generate_ini_N1(basic_info, ini.opt, log_N1)

mean_rec_par <- lapply(1:n_stocks, function(i) exp(log_N1[i]))

NAA_re <- list(
  N1_model = rep(ini.opt, n_stocks),
  sigma = rep(sigma, n_stocks),
  cor = rep(re_cor, n_stocks),
  recruit_model = 2,
  recruit_pars = mean_rec_par,
  sigma_vals = sigma_vals,
  N1_pars = N1_pars
)
```

### Generate WHAM input

```{r}
input <- prepare_wham_input(
  basic_info = basic_info,
  selectivity = sel,
  NAA_re = NAA_re,
  move = move,
  catch_info = catch_info,
  index_info = index_info,
  F = F_info,
  age_comp = "logistic-normal-miss0"
)
```

### Generate OM

```{r}
random <- input$random
input$random <- NULL
om <- fit_wham(input, do.fit = FALSE, do.brps = TRUE, MakeADFun.silent = TRUE)
```

### Configure assessment timing

```{r}
assess.interval <- 3
base.years      <- year_start:year_end
terminal.year   <- tail(base.years, 1)
assess.years    <- seq(terminal.year, tail(om$years, 1) - assess.interval, by = assess.interval)
mods <- list()
```

### Re-configure selectivity and NAA

```{r}
n_stocks = n_regions = n_fleets = n_indices = 1

sel_em <- list(model=rep("logistic", n_fleets + n_indices),
               initial_pars=c(rep(list(fleet_pars), n_fleets), rep(list(index_pars), n_indices)))

NAA_re_em <- list(N1_model="equilibrium", sigma="rec+1", cor="iid")
```

## Run MSE scenarios

### EM1 is all one area for stock and fleets, 75% FXSPR

```{r}
om_with_data <- update_om_fn(om, seed = 123, random = random)

hcr <- list()
hcr$hcr.type <- 1
hcr$hcr.opts <- list(use_FXSPR = TRUE, percentFXSPR = 75)

mods[[1]] = loop_through_fn(om = om_with_data,
                            em_info = info,
                            random = random,
                            sel_em = sel_em,
                            NAA_re_em = NAA_re_em,
                            move_em = NULL,
                            age_comp_em = "logistic-normal-miss0",
                            em.opt = list(separate.em = TRUE, separate.em.type = 1, do.move = FALSE, est.move = FALSE),
                            aggregate_catch_info = list(n_fleets = 1, fleet_pointer = c(1,1), use_catch_weighted_waa = TRUE, catch_Neff = 100, catch_cv = 0.1),
                            aggregate_index_info = list(n_indices = 1, index_pointer = c(1,1), use_catch_weighted_waa = TRUE, index_Neff = 100, index_cv = 0.1),
                            hcr = hcr,
                            assess_years = assess.years,
                            assess_interval = assess.interval,
                            base_years = base.years,
                            year.use = 20,
                            seed = 123)
```

### EM2 is all one area for stock and fleets, 100% FXSPR

```{r}
hcr <- list()
hcr$hcr.type <- 1
hcr$hcr.opts <- list(use_FXSPR = TRUE, percentFXSPR = 100)

mods[[2]] = loop_through_fn(om = om_with_data,
                            em_info = info,
                            random = random,
                            sel_em = sel_em,
                            NAA_re_em = NAA_re_em,
                            move_em = NULL,
                            age_comp_em = "logistic-normal-miss0",
                            em.opt = list(separate.em = TRUE, separate.em.type = 1, do.move = FALSE, est.move = FALSE),
                            aggregate_catch_info = list(n_fleets = 1, fleet_pointer = c(1,1), use_catch_weighted_waa = TRUE, catch_Neff = 100, catch_cv = 0.1),
                            aggregate_index_info = list(n_indices = 1, index_pointer = c(1,1), use_catch_weighted_waa = TRUE, index_Neff = 100, index_cv = 0.1),
                            hcr = hcr,
                            assess_years = assess.years,
                            assess_interval = assess.interval,
                            base_years = base.years,
                            year.use = 20,
                            seed = 123)
```


### EM3 is all one area for stock and fleets, hockey stick HCR

```{r}
hcr <- list()
hcr$hcr.type <- 3
hcr$hcr.opts <- list(use_FXSPR = TRUE, max_percent = 80, min_percent = 0.01, BThresh_up = 0.5, BThresh_low = 0)

mods[[3]] = loop_through_fn(om = om_with_data,
                            em_info = info,
                            random = random,
                            sel_em = sel_em,
                            NAA_re_em = NAA_re_em,
                            move_em = NULL,
                            age_comp_em = "logistic-normal-miss0",
                            em.opt = list(separate.em = TRUE, separate.em.type = 1, do.move = FALSE, est.move = FALSE),
                            aggregate_catch_info = list(n_fleets = 1, fleet_pointer = c(1,1), use_catch_weighted_waa = TRUE, catch_Neff = 100, catch_cv = 0.1),
                            aggregate_index_info = list(n_indices = 1, index_pointer = c(1,1), use_catch_weighted_waa = TRUE, index_Neff = 100, index_cv = 0.1),
                            hcr = hcr,
                            assess_years = assess.years,
                            assess_interval = assess.interval,
                            base_years = base.years,
                            year.use = 20,
                            seed = 123)
```

## Compare performance

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

yrs <- 1:23

# Create dataframe
df <- data.frame(
  Year = yrs,
  SSB_EM1 = mods[[1]]$om$rep$SSB[1:23,1],
  SSB_EM2 = mods[[2]]$om$rep$SSB[1:23,1],
  SSB_EM3 = mods[[3]]$om$rep$SSB[1:23,1],
  Catch_EM1 = mods[[1]]$om$rep$pred_catch[1:23,1],
  Catch_EM2 = mods[[2]]$om$rep$pred_catch[1:23,1],
  Catch_EM3 = mods[[3]]$om$rep$pred_catch[1:23,1]
)

# Convert to long format
plot_df <- df |>
  pivot_longer(-Year) |>
  separate(name, into = c("Variable","Model"), sep = "_")

plot_df$Model <- factor(plot_df$Model,
                        levels = c("EM1","EM2","EM3"),
                        labels = c("EM 1","EM 2","EM 3"))

# Plot
ggplot(plot_df, aes(Year, value, color = Model)) +
  geom_line() +
  geom_point() +
  facet_wrap(~Variable, scales = "free_y") +
  scale_color_manual(values = c("red","blue","green")) +
  labs(
    x = "Year",
    y = NULL
  ) +
  theme_bw() +
  theme(
    strip.text = element_text(face = "bold"),
    legend.position = "top"
  )
```

Same results as vignette using the official SPASAM.MSE, all good. 

OK, now try this with a local build of SPASAM.MSE from my fork that has an updated `advice_fn.R` file

First I'm rerunning the above code to ensure I haven't broken the existing functions.

Still the same results, good.

Now add HCR 4

## Some notes on HCR 4

The MAFMC risk policy and control rule require estimation both of stock B status and OFL based on an F reference point to estimate ABC

The Mid-Atlantic ABC control rule is based on the MAFMC risk policy for probability of overfishing, pstar, combined with the uncertainty in the OFL, OFL CV. It was updated in 2020 to include higher risk tolerance at high stock size. 

```{r MAFMCriskpolicy, fig.asp = 0.7}

riskpol <- data.frame(Bfrac = c(0, 0.1, 1.0, 1.5, 2.5),
                      Current = c(0, 0, 0.45, 0.49, 0.49),
                      Pre2020 = c(0, 0, 0.4, 0.4, 0.4)
)

riskpol <- riskpol %>%
  pivot_longer(-Bfrac, names_to = "pstar")

p1 <- ggplot2::ggplot(riskpol, aes(x=Bfrac, y=value, linetype = pstar)) +
  geom_path(show.legend = TRUE) +
  theme_minimal() +
  xlab("B/Bmsy") +
  ylab("p*") +
  labs(linetype = "Policy")+
  theme(legend.position="bottom")


#print(p1, vp=grid::viewport(gp=grid::gpar(cex=1.5)))
```


```{r OFLCVtoABC, fig.asp = 0.7}

ABCprop <- data.frame(Bfrac = seq(0, 2.5, 0.01)) %>%
  dplyr::mutate(pstar = case_when(Bfrac <= 0.1 ~ 0,
                                  Bfrac > 0.1 & Bfrac <= 1.0 ~ (Bfrac-0.1)*((0.45-0)/(1-0.1)) ,
                                  Bfrac > 1.0 & Bfrac <= 1.5 ~ (Bfrac-1.0)*((0.49-0.45)/(1.5-1))+0.45,
                                  Bfrac > 1.5 ~ 0.49)) %>%
  dplyr::mutate("CV=60%" = qlnorm(pstar, log(1), log(0.60 + 1)),
                "CV=100%" = qlnorm(pstar, log(1), log(1.00 + 1)),
                "CV=150%" = qlnorm(pstar, log(1), log(1.50 + 1))) %>%
  pivot_longer(-c(Bfrac, pstar), names_to = "CVlevel")
                       

p2 <- ggplot2::ggplot(ABCprop, aes(x=Bfrac, y=value, colour=CVlevel)) +
  geom_line()+  
  theme_minimal() +
  xlab("B/Bmsy") +
  ylab("ABC/OFL proportion") +
  labs(colour = "OFL CV") +
  theme(legend.position="bottom")

#print(p2, vp=grid::viewport(gp=grid::gpar(cex=1.5)))
  
```

```{r, fig.asp = 0.5}
library(patchwork)
p1 + p2
```

In WHAM the ABC can be used in projection as an input catch, but it is needed for each projection year, requiring multiple iterative projections.

My first attempts worked for 1 year projections but we would like more flexibility.

The NEFSC has some [code that does multiyear projections for WHAM models](https://github.com/NEFSC/READ-PDB-COLLABORATIONS/blob/main/Reference-Points-and-Projections/P-star.basic.model.R) which was generalized for use here.

```{r eval=FALSE}
# from https://github.com/NEFSC/READ-PDB-COLLABORATIONS/blob/main/Reference-Points-and-Projections/P-star.basic.model.R

# there are separate functions to estimate Pstar and ABC 
# this is the loop to fill a catch vector for projection in WHAM

# Specify the model and projection years
  model.years <- mod$years
  proj.years <- c((tail(model.years,1)+1):(tail(model.years,1)+projyr))
  
  # Empty variables to collect catch and pstar values
  catch.proj <- rep(0,projyr)
  
  # Catch in the first year of projections is specified
  catch.proj[1] <- catch.year1
  
  if(projyr>1)
  {  for(i in 1:(projyr-1))
    {
      # Tell WHAM to do projection based on catch in first i years ('5') and Fmsy proxy ('3') in following years
      proj_F_opt <- c(rep(5,i),rep(3,projyr-i))
      mod.proj <- project_wham(mod, proj.opts = list(n.yrs = projyr,proj_F_opt = proj_F_opt, proj_Fcatch = catch.proj), check.version = F)
      
      # Get OFL, SSB, and SSB ratio (relative to SSBMSY)
      ofl <- tail(apply(mod.proj$rep$pred_catch,1,sum),projyr)[i+1]
      ssb <- tail(apply(mod.proj$rep$SSB,1,sum),projyr)[i]
      ssbratio <- ssb/SSBmsy
      
      # Calculate catch from p* code
      catch <- ABC(ofl,ssbratio,CV)
      
      # As long as its not the terminal year, add the abc catch to catch vector and repeat
      if(i<projyr)
      {
        catch.proj[i+1] <- catch
        if(!is.null(avg.abc)) catch.proj[i+1] <- avg.abc
      }
    }
  }
  
  # Conduct one last projection to get F and SSB resultant from final ABC
  proj_F_opt <- c(rep(5,projyr))
  mod.proj <- project_wham(mod, proj.opts = list(n.yrs = projyr,proj_F_opt = proj_F_opt, proj_Fcatch = catch.proj), check.version = F)

  # Return the final projection model
  return(mod.proj)
```

The new `advice_fun.R` with the MAFMC risk policy plus HCR is here: https://github.com/sgaichas/SPASAM.MSE/blob/main/R/advice_fn.R


### EM4 is all one area for stock and fleets, MAFMC risk policy and HCR

```{r}
hcr <- list()
hcr$hcr.type <- 4
hcr$hcr.opts <- list(use_FXSPR = TRUE) #defaults

# Error in `advice_fn()`: length of proj.catch is not = number of projection years
# see if it can do one year projection first
#assess.interval <- 1

# it can, we need to fill the catch vector with assess.interval catches by projecting OFL based on ABC for each previous year
# the advice_fn needs to loop over years for this one?

mods[[4]] = loop_through_fn(om = om_with_data,
                            em_info = info,
                            random = random,
                            sel_em = sel_em,
                            NAA_re_em = NAA_re_em,
                            move_em = NULL,
                            age_comp_em = "logistic-normal-miss0",
                            em.opt = list(separate.em = TRUE, separate.em.type = 1, do.move = FALSE, est.move = FALSE),
                            aggregate_catch_info = list(n_fleets = 1, fleet_pointer = c(1,1), use_catch_weighted_waa = TRUE, catch_Neff = 100, catch_cv = 0.1),
                            aggregate_index_info = list(n_indices = 1, index_pointer = c(1,1), use_catch_weighted_waa = TRUE, index_Neff = 100, index_cv = 0.1),
                            hcr = hcr,
                            assess_years = assess.years,
                            assess_interval = assess.interval,
                            base_years = base.years,
                            year.use = 20,
                            seed = 123)
```

### EM5 is all one area for stock and fleets, MAFMC risk policy and HCR with 200% OFL CV

At B>Bmsy this wont make much difference but does result in slightly lower catch advice as predicted

```{r}
hcr <- list()
hcr$hcr.type <- 4
hcr$hcr.opts <- list(use_FXSPR = TRUE, OFL_CV = 2.0) #defaults but double OFL CV

# Error in `advice_fn()`: length of proj.catch is not = number of projection years
# see if it can do one year projection first
#assess.interval <- 1

# it can, we need to fill the catch vector with assess.interval catches by projecting OFL based on ABC for each previous year
# the advice_fn needs to loop over years for this one?

mods[[5]] = loop_through_fn(om = om_with_data,
                            em_info = info,
                            random = random,
                            sel_em = sel_em,
                            NAA_re_em = NAA_re_em,
                            move_em = NULL,
                            age_comp_em = "logistic-normal-miss0",
                            em.opt = list(separate.em = TRUE, separate.em.type = 1, do.move = FALSE, est.move = FALSE),
                            aggregate_catch_info = list(n_fleets = 1, fleet_pointer = c(1,1), use_catch_weighted_waa = TRUE, catch_Neff = 100, catch_cv = 0.1),
                            aggregate_index_info = list(n_indices = 1, index_pointer = c(1,1), use_catch_weighted_waa = TRUE, index_Neff = 100, index_cv = 0.1),
                            hcr = hcr,
                            assess_years = assess.years,
                            assess_interval = assess.interval,
                            base_years = base.years,
                            year.use = 20,
                            seed = 123)
```


## Compare performance with MAFMC HCR

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

yrs <- 1:23

# Create dataframe
df <- data.frame(
  Year = yrs,
  SSB_EM1 = mods[[1]]$om$rep$SSB[1:23,1],
  SSB_EM2 = mods[[2]]$om$rep$SSB[1:23,1],
  SSB_EM3 = mods[[3]]$om$rep$SSB[1:23,1],
  SSB_EM4 = mods[[4]]$om$rep$SSB[1:23,1],
  SSB_EM5 = mods[[5]]$om$rep$SSB[1:23,1],
  Catch_EM1 = mods[[1]]$om$rep$pred_catch[1:23,1],
  Catch_EM2 = mods[[2]]$om$rep$pred_catch[1:23,1],
  Catch_EM3 = mods[[3]]$om$rep$pred_catch[1:23,1],
  Catch_EM4 = mods[[4]]$om$rep$pred_catch[1:23,1],
  Catch_EM5 = mods[[5]]$om$rep$pred_catch[1:23,1]
)

# Convert to long format
plot_df <- df |>
  pivot_longer(-Year) |>
  separate(name, into = c("Variable","Model"), sep = "_")

plot_df$Model <- factor(plot_df$Model,
                        levels = c("EM1","EM2","EM3", "EM4", "EM5"),
                        labels = c("EM 1","EM 2","EM 3", "EM 4", "EM 5"))

# Plot
ggplot(plot_df, aes(Year, value, color = Model)) +
  geom_line() +
  geom_point() +
  facet_wrap(~Variable, scales = "free_y") +
  scale_color_manual(values = c("red","blue","green", "purple", "brown")) +
  labs(
    x = "Year",
    y = NULL
  ) +
  theme_bw() +
  theme(
    strip.text = element_text(face = "bold"),
    legend.position = "top"
  )
```
## Make sure it runs for more than one assessment cycle

### EM6 is all one area for stock and fleets, MAFMC risk policy and HCR for 3 cycles

Start over with MSE_years = 9

```{r, eval=FALSE}

year_start  <- 1
year_end    <- 20
MSE_years   <- 9

info <- generate_basic_info(
  n_stocks = 2,
  n_regions = 2,
  n_indices = 2,
  n_fleets = 2,
  n_seasons = 1,
  base.years = year_start:year_end,
  n_feedback_years = MSE_years,
  life_history = "medium",
  n_ages = 12
)

basic_info = info$basic_info
catch_info = info$catch_info
index_info = info$index_info
F_info     = info$F

basic_info <- generate_NAA_where(basic_info, move.type = 2)
move <- generate_move(
  basic_info = basic_info,
  move.type = 2,
  move.rate = c(0.3, 0.1),
  move.re = "constant"
)

n_stocks  <- as.integer(basic_info['n_stocks'])
n_regions <- as.integer(basic_info['n_regions'])
n_fleets  <- as.integer(basic_info['n_fleets'])
n_indices <- as.integer(basic_info['n_indices'])
n_ages    <- as.integer(basic_info['n_ages'])

fleet_pars <- c(5, 1)
index_pars <- c(2, 1)
sel <- list(
  model = rep("logistic", n_fleets + n_indices),
  initial_pars = c(rep(list(fleet_pars), n_fleets), rep(list(index_pars), n_indices))
)

sigma      <- "rec+1"
re_cor     <- "iid"
ini.opt    <- "equilibrium"
Rec_sig    <- 0.5
NAA_sig    <- 0.2

sigma_vals <- array(NAA_sig, dim = c(n_stocks, n_regions, n_ages))
sigma_vals[,,1] <- Rec_sig

log_N1    <- rep(10, n_stocks)
log_N1[1] <- log(exp(10) * 2)
N1_pars   <- generate_ini_N1(basic_info, ini.opt, log_N1)

mean_rec_par <- lapply(1:n_stocks, function(i) exp(log_N1[i]))

NAA_re <- list(
  N1_model = rep(ini.opt, n_stocks),
  sigma = rep(sigma, n_stocks),
  cor = rep(re_cor, n_stocks),
  recruit_model = 2,
  recruit_pars = mean_rec_par,
  sigma_vals = sigma_vals,
  N1_pars = N1_pars
)

input <- prepare_wham_input(
  basic_info = basic_info,
  selectivity = sel,
  NAA_re = NAA_re,
  move = move,
  catch_info = catch_info,
  index_info = index_info,
  F = F_info,
  age_comp = "logistic-normal-miss0"
)


random <- input$random
input$random <- NULL
om <- fit_wham(input, do.fit = FALSE, do.brps = TRUE, MakeADFun.silent = TRUE)

assess.interval <- 3
base.years      <- year_start:year_end
terminal.year   <- tail(base.years, 1)
assess.years    <- seq(terminal.year, tail(om$years, 1) - assess.interval, by = assess.interval)


n_stocks = n_regions = n_fleets = n_indices = 1

sel_em <- list(model=rep("logistic", n_fleets + n_indices),
               initial_pars=c(rep(list(fleet_pars), n_fleets), rep(list(index_pars), n_indices)))

NAA_re_em <- list(N1_model="equilibrium", sigma="rec+1", cor="iid")

hcr <- list()
hcr$hcr.type <- 4
hcr$hcr.opts <- list(use_FXSPR = TRUE) #defaults but double OFL CV


mods[[6]] = loop_through_fn(om = om_with_data,
                            em_info = info,
                            random = random,
                            sel_em = sel_em,
                            NAA_re_em = NAA_re_em,
                            move_em = NULL,
                            age_comp_em = "logistic-normal-miss0",
                            em.opt = list(separate.em = TRUE, separate.em.type = 1, do.move = FALSE, est.move = FALSE),
                            aggregate_catch_info = list(n_fleets = 1, fleet_pointer = c(1,1), use_catch_weighted_waa = TRUE, catch_Neff = 100, catch_cv = 0.1),
                            aggregate_index_info = list(n_indices = 1, index_pointer = c(1,1), use_catch_weighted_waa = TRUE, index_Neff = 100, index_cv = 0.1),
                            hcr = hcr,
                            assess_years = assess.years,
                            assess_interval = assess.interval,
                            base_years = base.years,
                            year.use = 20,
                            seed = 123)
```

This errors out, copied output below

```
  --------------------
  
  IMPORTANT!!!!
  
  For the current version of WHAM, if WAA pointers are specified (i.e., WAA differs across fleets, indices, or stocks),
  
  they need to be updated *after* prepare_wham_input(). Otherwise, a global WAA will be applied to all components.
          
  --------------------
          

  --------------------
  IMPORTANT!!!!
  
  For the current version of WHAM:
  
  - If CV and effective sample size for **catch** vary over years,
  or if some years have missing aggregate or age composition data for **catch**,
  you must update these inputs *after* prepare_wham_input()
  using the update_input_catch_info() function.
  
  - If CV and effective sample size for **indices** vary over years,
  or if some years have missing aggregate or age composition data for **indices**,
  you must update these inputs *after* prepare_wham_input()
  using the update_input_index_info() function.
  
  Otherwise, WHAM will assume constant CV/sample size and complete data across all years.
  --------------------
          
Note: Movement rate is assumed to be region-specific regardless of stock!

All stocks 'can' move

Movement rate for stocks in region 1 is 0.3

Movement rate for stocks in region 2 is 0.1

Movement is assumed at a constant rate without random effects

--Creating input---------------------------------------------------------------------------------------------------------------------

basic_info done
catch done
indices done
WAA done
NAA done
q done
selectivity done
age_comp done
F done
M done
move done
osa_obs done

--Input Complete--------------------------------------------------------------------------------------------------------------------

-------------------------------------------------------------------------------------------------------------------------------------
WHAM version 2.0.0 and forward: 
1) makes major changes to the structure of some data, parameters, and reported objects.
2) decouples random effects for recruitment and random effects for older ages by default. To obtain results from previous versions set NAA_re$decouple_recruitment = FALSE.
3) does not bias correct any log-normal process or observation errors. To configure these, set basic_info$bias_correct_process = TRUE and/or basic_info$bias_correct_observation = TRUE.
-------------------------------------------------------------------------------------------------------------------------------------
input$data$spawn_regions will be defined from input$data$NAA_where for age 1.
--Catch------------------------------------------------------------------------------------------------------------------------------ 
catch_info$waa_pointer_fleets was not provided, so the first waa matrix will be used for all fleets. 
Selectivity blocks for each fleet:
Fleet 1: 1
Fleet 2: 2

-------------------------------------------------------------------------------------------------------------------------------------

--Indices----------------------------------------------------------------------------------------------------------------------------
Selectivity blocks for each index:
index_1: 3
index_2: 4

-------------------------------------------------------------------------------------------------------------------------------------

--Selectivity------------------------------------------------------------------------------------------------------------------------
selectivity$n_selblocks was not provided so number of selblocks: 4, is being determined by max(input$data$selblock_pointer_fleets,input$data$selblock_pointer_indices).
(Mean) selectivity block models are:
Block 1: logistic
Block 2: logistic
Block 3: logistic
Block 4: logistic

Random effects options for each selectivity block are:
Block 1: none
Block 2: none
Block 3: none
Block 4: none

-------------------------------------------------------------------------------------------------------------------------------------

--Movement---------------------------------------------------------------------------------------------------------------------------
movement and mortality will be assumed to occur sequentially within each season.
-------------------------------------------------------------------------------------------------------------------------------------

--Reference points-------------------------------------------------------------------------------------------------------------------
For annual SPR-based reference points, corresponding annual conditionally expected recruitments are used. 
-------------------------------------------------------------------------------------------------------------------------------------
Now conducting stock assessment for year 20
Using user-specified WAA array. WAA can be time-varying.

  --------------------
  
  IMPORTANT!!!!
  
  For the current version of WHAM, if WAA pointers are specified (i.e., WAA differs across fleets, indices, or stocks),
  
  they need to be updated *after* prepare_wham_input(). Otherwise, a global WAA will be applied to all components.
          
  --------------------
          

  --------------------
  IMPORTANT!!!!
  
  For the current version of WHAM:
  
  - If CV and effective sample size for **catch** vary over years,
  or if some years have missing aggregate or age composition data for **catch**,
  you must update these inputs *after* prepare_wham_input()
  using the update_input_catch_info() function.
  
  - If CV and effective sample size for **indices** vary over years,
  or if some years have missing aggregate or age composition data for **indices**,
  you must update these inputs *after* prepare_wham_input()
  using the update_input_index_info() function.
  
  Otherwise, WHAM will assume constant CV/sample size and complete data across all years.
  --------------------
          

--Creating input---------------------------------------------------------------------------------------------------------------------

basic_info done
catch done
indices done
WAA done
NAA done
q done
selectivity done
age_comp done
F done
M done
move done
osa_obs done

--Input Complete--------------------------------------------------------------------------------------------------------------------

-------------------------------------------------------------------------------------------------------------------------------------
WHAM version 2.0.0 and forward: 
1) makes major changes to the structure of some data, parameters, and reported objects.
2) decouples random effects for recruitment and random effects for older ages by default. To obtain results from previous versions set NAA_re$decouple_recruitment = FALSE.
3) does not bias correct any log-normal process or observation errors. To configure these, set basic_info$bias_correct_process = TRUE and/or basic_info$bias_correct_observation = TRUE.
-------------------------------------------------------------------------------------------------------------------------------------
input$data$spawn_regions will be defined from input$data$NAA_where for age 1.
--Catch------------------------------------------------------------------------------------------------------------------------------ 
catch_info$waa_pointer_fleets was not provided, so the first waa matrix will be used for all fleets. 
Selectivity blocks for each fleet:
Fleet 1: 1

-------------------------------------------------------------------------------------------------------------------------------------

--Indices----------------------------------------------------------------------------------------------------------------------------
Selectivity blocks for each index:
index_1: 2

-------------------------------------------------------------------------------------------------------------------------------------

--NAA--------------------------------------------------------------------------------------------------------------------------------

 Same NAA_re$sigma being used for all stocks (rec+1).
-------------------------------------------------------------------------------------------------------------------------------------

--Selectivity------------------------------------------------------------------------------------------------------------------------
selectivity$n_selblocks was not provided so number of selblocks: 2, is being determined by max(input$data$selblock_pointer_fleets,input$data$selblock_pointer_indices).
(Mean) selectivity block models are:
Block 1: logistic
Block 2: logistic

Random effects options for each selectivity block are:
Block 1: none
Block 2: none

-------------------------------------------------------------------------------------------------------------------------------------

--Reference points-------------------------------------------------------------------------------------------------------------------
For annual SPR-based reference points, corresponding annual conditionally expected recruitments are used. 
-------------------------------------------------------------------------------------------------------------------------------------



    
    --------------------
    
    IMPORTANT!!!
    
    WAA pointers are updated!
    
    --------------------
            
Now fitting assessment model...
Using stats::nlminb for optimization with these control parameters:
iter.max: 1000
eval.max: 1000
Now checking convergence of assessment model...

Assessment model is converged.

Now using the EM to project catch...

Harvest Control Rule type 4
SSB_t / SSB_XSPR = 1.421 -> pstar = 0.48; OFL = 27265.870
SSB_t / SSB_XSPR = 1.190 -> pstar = 0.47; OFL = 23301.292
SSB_t / SSB_XSPR = 1.216 -> pstar = 0.47; OFL = 23844.105
Final Projection Options:
 n.yrs: 3
 use.last.F: FALSE
 use.avg.F: FALSE
 use.FXSPR: FALSE
 use.FMSY: FALSE
 avg.yrs: 16, 17, 18, 19, 20
 cont.ecov: TRUE
 use.last.ecov: FALSE
 cont.M.re: FALSE
 cont.L.re: FALSE
 proj.catch: 26502.4851487604, 21933.1863659308, 22524.8192760094

Projected catch from assessment model is
         [,1]
[1,] 26502.49
[2,] 21933.19
[3,] 22524.82

Now allocating catch...

Now generating catch advice...
         Fleet_1  Fleet_2
Year_21 13251.24 13251.24
Year_22 10966.59 10966.59
Year_23 11262.41 11262.41

Now calculating F at age in the OM given the catch advice...

Now calculating fleet-specific F in year 21

Fishing mortality is 2.82679025789732, 0.486816407205427

Now updating F in OM for year 21

Now simulating data for year 21

Now projecting data for years after 21

Now calculating fleet-specific F in year 22

Fishing mortality is 10, 0.592861858351235

Now updating F in OM for year 22

Now simulating data for year 22

Now projecting data for years after 22

Now calculating fleet-specific F in year 23

Fishing mortality is 10, 0.91613094355955

Now updating F in OM for year 23

Now simulating data for year 23

Now projecting data for years after 23

Now conducting stock assessment for year 23
Using user-specified WAA array. WAA can be time-varying.

  --------------------
  
  IMPORTANT!!!!
  
  For the current version of WHAM, if WAA pointers are specified (i.e., WAA differs across fleets, indices, or stocks),
  
  they need to be updated *after* prepare_wham_input(). Otherwise, a global WAA will be applied to all components.
          
  --------------------
          

  --------------------
  IMPORTANT!!!!
  
  For the current version of WHAM:
  
  - If CV and effective sample size for **catch** vary over years,
  or if some years have missing aggregate or age composition data for **catch**,
  you must update these inputs *after* prepare_wham_input()
  using the update_input_catch_info() function.
  
  - If CV and effective sample size for **indices** vary over years,
  or if some years have missing aggregate or age composition data for **indices**,
  you must update these inputs *after* prepare_wham_input()
  using the update_input_index_info() function.
  
  Otherwise, WHAM will assume constant CV/sample size and complete data across all years.
  --------------------
          

--Creating input---------------------------------------------------------------------------------------------------------------------

basic_info done
catch done
indices done
WAA done
NAA done
q done
selectivity done
age_comp done
F done
M done
move done
osa_obs done

--Input Complete--------------------------------------------------------------------------------------------------------------------

-------------------------------------------------------------------------------------------------------------------------------------
WHAM version 2.0.0 and forward: 
1) makes major changes to the structure of some data, parameters, and reported objects.
2) decouples random effects for recruitment and random effects for older ages by default. To obtain results from previous versions set NAA_re$decouple_recruitment = FALSE.
3) does not bias correct any log-normal process or observation errors. To configure these, set basic_info$bias_correct_process = TRUE and/or basic_info$bias_correct_observation = TRUE.
-------------------------------------------------------------------------------------------------------------------------------------
input$data$spawn_regions will be defined from input$data$NAA_where for age 1.
--Catch------------------------------------------------------------------------------------------------------------------------------ 
catch_info$waa_pointer_fleets was not provided, so the first waa matrix will be used for all fleets. 
Selectivity blocks for each fleet:
Fleet 1: 1

-------------------------------------------------------------------------------------------------------------------------------------

--Indices----------------------------------------------------------------------------------------------------------------------------
Selectivity blocks for each index:
index_1: 2

-------------------------------------------------------------------------------------------------------------------------------------

--NAA--------------------------------------------------------------------------------------------------------------------------------

 Same NAA_re$sigma being used for all stocks (rec+1).
-------------------------------------------------------------------------------------------------------------------------------------

--Selectivity------------------------------------------------------------------------------------------------------------------------
selectivity$n_selblocks was not provided so number of selblocks: 2, is being determined by max(input$data$selblock_pointer_fleets,input$data$selblock_pointer_indices).
(Mean) selectivity block models are:
Block 1: logistic
Block 2: logistic

Random effects options for each selectivity block are:
Block 1: none
Block 2: none

-------------------------------------------------------------------------------------------------------------------------------------

--Reference points-------------------------------------------------------------------------------------------------------------------
For annual SPR-based reference points, corresponding annual conditionally expected recruitments are used. 
-------------------------------------------------------------------------------------------------------------------------------------



    
    --------------------
    
    IMPORTANT!!!
    
    WAA pointers are updated!
    
    --------------------
            
Now fitting assessment model...
Using stats::nlminb for optimization with these control parameters:
iter.max: 1000
eval.max: 1000
Now checking convergence of assessment model...

Assessment model is converged.

Now using the EM to project catch...

Harvest Control Rule type 4
SSB_t / SSB_XSPR = 0.431 -> pstar = 0.17; OFL = 5157.838
SSB_t / SSB_XSPR = 0.596 -> pstar = 0.25; OFL = 7244.681
SSB_t / SSB_XSPR = 0.617 -> pstar = 0.26; OFL = 7539.261
Final Projection Options:
 n.yrs: 3
 use.last.F: FALSE
 use.avg.F: FALSE
 use.FXSPR: FALSE
 use.FMSY: FALSE
 avg.yrs: 19, 20, 21, 22, 23
 cont.ecov: TRUE
 use.last.ecov: FALSE
 cont.M.re: FALSE
 cont.L.re: FALSE
 proj.catch: 2628.61687778367, 4518.98136990777, 4811.51232909579

Projected catch from assessment model is
         [,1]
[1,] 2628.617
[2,] 4518.981
[3,] 4811.512

Now allocating catch...

Now generating catch advice...
         Fleet_1  Fleet_2
Year_24 1314.308 1314.308
Year_25 2259.491 2259.491
Year_26 2405.756 2405.756

Now calculating F at age in the OM given the catch advice...

Now calculating fleet-specific F in year 24
Warning in max(exp(rep$log_FAA_tot[year, ])) :
  no non-missing arguments to max; returning -Inf
Warning in max(rep$FAA[i, year, ]) :
  no non-missing arguments to max; returning -Inf
Warning in max(rep$FAA[i, year, ]) :
  no non-missing arguments to max; returning -Inf
Error in sel[f, a] : subscript out of bounds
```