---
title: "Test Harvest Control Rule"
author: "Sarah Gaichas"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(wham)
library(SPASAM.MSE)

main.dir = here::here()

```

# Code taken from the SPASM.MSE vignettes [here](https://lichengxue.github.io/SPASAM.MSE/index.html)

Starting with this one https://lichengxue.github.io/SPASAM.MSE/Harvest-Control-Rule.html

And modifying to test the addition of the MAFMC risk policy and ABC HCR to  `SPASAM.MSE::advice_fn()`

First run the code as is

## Operating model setup

### Basic information

```{r}
year_start  <- 1
year_end    <- 20
MSE_years   <- 3

info <- generate_basic_info(
  n_stocks = 2,
  n_regions = 2,
  n_indices = 2,
  n_fleets = 2,
  n_seasons = 1,
  base.years = year_start:year_end,
  n_feedback_years = MSE_years,
  life_history = "medium",
  n_ages = 12
)

basic_info = info$basic_info
catch_info = info$catch_info
index_info = info$index_info
F_info     = info$F
```

### Specify movement

```{r}
basic_info <- generate_NAA_where(basic_info, move.type = 2)
move <- generate_move(
  basic_info = basic_info,
  move.type = 2,
  move.rate = c(0.3, 0.1),
  move.re = "constant"
)
```

### Configure selectivity

```{r}
n_stocks  <- as.integer(basic_info['n_stocks'])
n_regions <- as.integer(basic_info['n_regions'])
n_fleets  <- as.integer(basic_info['n_fleets'])
n_indices <- as.integer(basic_info['n_indices'])
n_ages    <- as.integer(basic_info['n_ages'])

fleet_pars <- c(5, 1)
index_pars <- c(2, 1)
sel <- list(
  model = rep("logistic", n_fleets + n_indices),
  initial_pars = c(rep(list(fleet_pars), n_fleets), rep(list(index_pars), n_indices))
)
```

### Configure NAA

```{r}
sigma      <- "rec+1"
re_cor     <- "iid"
ini.opt    <- "equilibrium"
Rec_sig    <- 0.5
NAA_sig    <- 0.2

sigma_vals <- array(NAA_sig, dim = c(n_stocks, n_regions, n_ages))
sigma_vals[,,1] <- Rec_sig

log_N1    <- rep(10, n_stocks)
log_N1[1] <- log(exp(10) * 2)
N1_pars   <- generate_ini_N1(basic_info, ini.opt, log_N1)

mean_rec_par <- lapply(1:n_stocks, function(i) exp(log_N1[i]))

NAA_re <- list(
  N1_model = rep(ini.opt, n_stocks),
  sigma = rep(sigma, n_stocks),
  cor = rep(re_cor, n_stocks),
  recruit_model = 2,
  recruit_pars = mean_rec_par,
  sigma_vals = sigma_vals,
  N1_pars = N1_pars
)
```

### Generate WHAM input

```{r}
input <- prepare_wham_input(
  basic_info = basic_info,
  selectivity = sel,
  NAA_re = NAA_re,
  move = move,
  catch_info = catch_info,
  index_info = index_info,
  F = F_info,
  age_comp = "logistic-normal-miss0"
)
```

### Generate OM

```{r}
random <- input$random
input$random <- NULL
om <- fit_wham(input, do.fit = FALSE, do.brps = TRUE, MakeADFun.silent = TRUE)
```

### Configure assessment timing

```{r}
assess.interval <- 3
base.years      <- year_start:year_end
terminal.year   <- tail(base.years, 1)
assess.years    <- seq(terminal.year, tail(om$years, 1) - assess.interval, by = assess.interval)
mods <- list()
```

### Re-configure selectivity and NAA

```{r}
n_stocks = n_regions = n_fleets = n_indices = 1

sel_em <- list(model=rep("logistic", n_fleets + n_indices),
               initial_pars=c(rep(list(fleet_pars), n_fleets), rep(list(index_pars), n_indices)))

NAA_re_em <- list(N1_model="equilibrium", sigma="rec+1", cor="iid")
```

## Run MSE scenarios

### EM1 is all one area for stock and fleets, 75% FXSPR

```{r}
om_with_data <- update_om_fn(om, seed = 123, random = random)

hcr <- list()
hcr$hcr.type <- 1
hcr$hcr.opts <- list(use_FXSPR = TRUE, percentFXSPR = 75)

mods[[1]] = loop_through_fn(om = om_with_data,
                            em_info = info,
                            random = random,
                            sel_em = sel_em,
                            NAA_re_em = NAA_re_em,
                            move_em = NULL,
                            age_comp_em = "logistic-normal-miss0",
                            em.opt = list(separate.em = TRUE, separate.em.type = 1, do.move = FALSE, est.move = FALSE),
                            aggregate_catch_info = list(n_fleets = 1, fleet_pointer = c(1,1), use_catch_weighted_waa = TRUE, catch_Neff = 100, catch_cv = 0.1),
                            aggregate_index_info = list(n_indices = 1, index_pointer = c(1,1), use_catch_weighted_waa = TRUE, index_Neff = 100, index_cv = 0.1),
                            hcr = hcr,
                            assess_years = assess.years,
                            assess_interval = assess.interval,
                            base_years = base.years,
                            year.use = 20,
                            seed = 123)
```

### EM2 is all one area for stock and fleets, 100% FXSPR

```{r}
hcr <- list()
hcr$hcr.type <- 1
hcr$hcr.opts <- list(use_FXSPR = TRUE, percentFXSPR = 100)

mods[[2]] = loop_through_fn(om = om_with_data,
                            em_info = info,
                            random = random,
                            sel_em = sel_em,
                            NAA_re_em = NAA_re_em,
                            move_em = NULL,
                            age_comp_em = "logistic-normal-miss0",
                            em.opt = list(separate.em = TRUE, separate.em.type = 1, do.move = FALSE, est.move = FALSE),
                            aggregate_catch_info = list(n_fleets = 1, fleet_pointer = c(1,1), use_catch_weighted_waa = TRUE, catch_Neff = 100, catch_cv = 0.1),
                            aggregate_index_info = list(n_indices = 1, index_pointer = c(1,1), use_catch_weighted_waa = TRUE, index_Neff = 100, index_cv = 0.1),
                            hcr = hcr,
                            assess_years = assess.years,
                            assess_interval = assess.interval,
                            base_years = base.years,
                            year.use = 20,
                            seed = 123)
```


### EM3 is all one area for stock and fleets, hockey stick HCR

```{r}
hcr <- list()
hcr$hcr.type <- 3
hcr$hcr.opts <- list(use_FXSPR = TRUE, max_percent = 80, min_percent = 0.01, BThresh_up = 0.5, BThresh_low = 0)

mods[[3]] = loop_through_fn(om = om_with_data,
                            em_info = info,
                            random = random,
                            sel_em = sel_em,
                            NAA_re_em = NAA_re_em,
                            move_em = NULL,
                            age_comp_em = "logistic-normal-miss0",
                            em.opt = list(separate.em = TRUE, separate.em.type = 1, do.move = FALSE, est.move = FALSE),
                            aggregate_catch_info = list(n_fleets = 1, fleet_pointer = c(1,1), use_catch_weighted_waa = TRUE, catch_Neff = 100, catch_cv = 0.1),
                            aggregate_index_info = list(n_indices = 1, index_pointer = c(1,1), use_catch_weighted_waa = TRUE, index_Neff = 100, index_cv = 0.1),
                            hcr = hcr,
                            assess_years = assess.years,
                            assess_interval = assess.interval,
                            base_years = base.years,
                            year.use = 20,
                            seed = 123)
```

## Compare performance

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

yrs <- 1:23

# Create dataframe
df <- data.frame(
  Year = yrs,
  SSB_EM1 = mods[[1]]$om$rep$SSB[1:23,1],
  SSB_EM2 = mods[[2]]$om$rep$SSB[1:23,1],
  SSB_EM3 = mods[[3]]$om$rep$SSB[1:23,1],
  Catch_EM1 = mods[[1]]$om$rep$pred_catch[1:23,1],
  Catch_EM2 = mods[[2]]$om$rep$pred_catch[1:23,1],
  Catch_EM3 = mods[[3]]$om$rep$pred_catch[1:23,1]
)

# Convert to long format
plot_df <- df |>
  pivot_longer(-Year) |>
  separate(name, into = c("Variable","Model"), sep = "_")

plot_df$Model <- factor(plot_df$Model,
                        levels = c("EM1","EM2","EM3"),
                        labels = c("EM 1","EM 2","EM 3"))

# Plot
ggplot(plot_df, aes(Year, value, color = Model)) +
  geom_line() +
  geom_point() +
  facet_wrap(~Variable, scales = "free_y") +
  scale_color_manual(values = c("red","blue","green")) +
  labs(
    x = "Year",
    y = NULL
  ) +
  theme_bw() +
  theme(
    strip.text = element_text(face = "bold"),
    legend.position = "top"
  )
```

Same results as vignette using the official SPASAM.MSE, all good. 

OK, now try this with a local build of SPASAM.MSE from my fork that has an updated `advice_fn.R` file

First I'm rerunning the above code to ensure I haven't broken the existing functions.

Still the same results, good.

Now add HCR 4

## Some notes on HCR 4

The MAFMC risk policy and control rule require estimation both of stock B status and OFL based on an F reference point to estimate ABC

The Mid-Atlantic ABC control rule is based on the MAFMC risk policy for probability of overfishing, pstar, combined with the uncertainty in the OFL, OFL CV. It was updated in 2020 to include higher risk tolerance at high stock size. 

```{r MAFMCriskpolicy, fig.asp = 0.7}

riskpol <- data.frame(Bfrac = c(0, 0.1, 1.0, 1.5, 2.5),
                      Current = c(0, 0, 0.45, 0.49, 0.49),
                      Pre2020 = c(0, 0, 0.4, 0.4, 0.4)
)

riskpol <- riskpol %>%
  pivot_longer(-Bfrac, names_to = "pstar")

p1 <- ggplot2::ggplot(riskpol, aes(x=Bfrac, y=value, linetype = pstar)) +
  geom_path(show.legend = TRUE) +
  theme_minimal() +
  xlab("B/Bmsy") +
  ylab("p*") +
  labs(linetype = "Policy")+
  theme(legend.position="bottom")


#print(p1, vp=grid::viewport(gp=grid::gpar(cex=1.5)))
```


```{r OFLCVtoABC, fig.asp = 0.7}

ABCprop <- data.frame(Bfrac = seq(0, 2.5, 0.01)) %>%
  dplyr::mutate(pstar = case_when(Bfrac <= 0.1 ~ 0,
                                  Bfrac > 0.1 & Bfrac <= 1.0 ~ (Bfrac-0.1)*((0.45-0)/(1-0.1)) ,
                                  Bfrac > 1.0 & Bfrac <= 1.5 ~ (Bfrac-1.0)*((0.49-0.45)/(1.5-1))+0.45,
                                  Bfrac > 1.5 ~ 0.49)) %>%
  dplyr::mutate("CV=60%" = qlnorm(pstar, log(1), log(0.60 + 1)),
                "CV=100%" = qlnorm(pstar, log(1), log(1.00 + 1)),
                "CV=150%" = qlnorm(pstar, log(1), log(1.50 + 1))) %>%
  pivot_longer(-c(Bfrac, pstar), names_to = "CVlevel")
                       

p2 <- ggplot2::ggplot(ABCprop, aes(x=Bfrac, y=value, colour=CVlevel)) +
  geom_line()+  
  theme_minimal() +
  xlab("B/Bmsy") +
  ylab("ABC/OFL proportion") +
  labs(colour = "OFL CV") +
  theme(legend.position="bottom")

#print(p2, vp=grid::viewport(gp=grid::gpar(cex=1.5)))
  
```

```{r, fig.asp = 0.5}
library(patchwork)
p1 + p2
```

In WHAM the ABC can be used in projection as an input catch, but it is needed for each projection year, requiring multiple iterative projections.

My first attempts worked for 1 year projections but we would like more flexibility.

The NEFSC has some [code that does multiyear projections for WHAM models](https://github.com/NEFSC/READ-PDB-COLLABORATIONS/blob/main/Reference-Points-and-Projections/P-star.basic.model.R) which was generalized for use here.

```{r eval=FALSE}
# from https://github.com/NEFSC/READ-PDB-COLLABORATIONS/blob/main/Reference-Points-and-Projections/P-star.basic.model.R

# there are separate functions to estimate Pstar and ABC 
# this is the loop to fill a catch vector for projection in WHAM

# Specify the model and projection years
  model.years <- mod$years
  proj.years <- c((tail(model.years,1)+1):(tail(model.years,1)+projyr))
  
  # Empty variables to collect catch and pstar values
  catch.proj <- rep(0,projyr)
  
  # Catch in the first year of projections is specified
  catch.proj[1] <- catch.year1
  
  if(projyr>1)
  {  for(i in 1:(projyr-1))
    {
      # Tell WHAM to do projection based on catch in first i years ('5') and Fmsy proxy ('3') in following years
      proj_F_opt <- c(rep(5,i),rep(3,projyr-i))
      mod.proj <- project_wham(mod, proj.opts = list(n.yrs = projyr,proj_F_opt = proj_F_opt, proj_Fcatch = catch.proj), check.version = F)
      
      # Get OFL, SSB, and SSB ratio (relative to SSBMSY)
      ofl <- tail(apply(mod.proj$rep$pred_catch,1,sum),projyr)[i+1]
      ssb <- tail(apply(mod.proj$rep$SSB,1,sum),projyr)[i]
      ssbratio <- ssb/SSBmsy
      
      # Calculate catch from p* code
      catch <- ABC(ofl,ssbratio,CV)
      
      # As long as its not the terminal year, add the abc catch to catch vector and repeat
      if(i<projyr)
      {
        catch.proj[i+1] <- catch
        if(!is.null(avg.abc)) catch.proj[i+1] <- avg.abc
      }
    }
  }
  
  # Conduct one last projection to get F and SSB resultant from final ABC
  proj_F_opt <- c(rep(5,projyr))
  mod.proj <- project_wham(mod, proj.opts = list(n.yrs = projyr,proj_F_opt = proj_F_opt, proj_Fcatch = catch.proj), check.version = F)

  # Return the final projection model
  return(mod.proj)
```

The new `advice_fun.R` with the MAFMC risk policy plus HCR is here: https://github.com/sgaichas/SPASAM.MSE/blob/main/R/advice_fn.R


### EM4 is all one area for stock and fleets, MAFMC risk policy and HCR

```{r}
hcr <- list()
hcr$hcr.type <- 4
hcr$hcr.opts <- list(use_FXSPR = TRUE) #defaults

# Error in `advice_fn()`: length of proj.catch is not = number of projection years
# see if it can do one year projection first
#assess.interval <- 1

# it can, we need to fill the catch vector with assess.interval catches by projecting OFL based on ABC for each previous year
# the advice_fn needs to loop over years for this one?

mods[[4]] = loop_through_fn(om = om_with_data,
                            em_info = info,
                            random = random,
                            sel_em = sel_em,
                            NAA_re_em = NAA_re_em,
                            move_em = NULL,
                            age_comp_em = "logistic-normal-miss0",
                            em.opt = list(separate.em = TRUE, separate.em.type = 1, do.move = FALSE, est.move = FALSE),
                            aggregate_catch_info = list(n_fleets = 1, fleet_pointer = c(1,1), use_catch_weighted_waa = TRUE, catch_Neff = 100, catch_cv = 0.1),
                            aggregate_index_info = list(n_indices = 1, index_pointer = c(1,1), use_catch_weighted_waa = TRUE, index_Neff = 100, index_cv = 0.1),
                            hcr = hcr,
                            assess_years = assess.years,
                            assess_interval = assess.interval,
                            base_years = base.years,
                            year.use = 20,
                            seed = 123)
```

## Compare performance with MAFMC HCR

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

yrs <- 1:23

# Create dataframe
df <- data.frame(
  Year = yrs,
  SSB_EM1 = mods[[1]]$om$rep$SSB[1:23,1],
  SSB_EM2 = mods[[2]]$om$rep$SSB[1:23,1],
  SSB_EM3 = mods[[3]]$om$rep$SSB[1:23,1],
  SSB_EM4 = mods[[4]]$om$rep$SSB[1:23,1],
  Catch_EM1 = mods[[1]]$om$rep$pred_catch[1:23,1],
  Catch_EM2 = mods[[2]]$om$rep$pred_catch[1:23,1],
  Catch_EM3 = mods[[3]]$om$rep$pred_catch[1:23,1],
  Catch_EM4 = mods[[4]]$om$rep$pred_catch[1:23,1]
)

# Convert to long format
plot_df <- df |>
  pivot_longer(-Year) |>
  separate(name, into = c("Variable","Model"), sep = "_")

plot_df$Model <- factor(plot_df$Model,
                        levels = c("EM1","EM2","EM3", "EM4"),
                        labels = c("EM 1","EM 2","EM 3", "EM 4"))

# Plot
ggplot(plot_df, aes(Year, value, color = Model)) +
  geom_line() +
  geom_point() +
  facet_wrap(~Variable, scales = "free_y") +
  scale_color_manual(values = c("red","blue","green", "purple")) +
  labs(
    x = "Year",
    y = NULL
  ) +
  theme_bw() +
  theme(
    strip.text = element_text(face = "bold"),
    legend.position = "top"
  )
```
