---
title: "Test Installation"
author: "Sarah Gaichas"
date: "`r Sys.Date()`"
output: html_document
---

# Code taken from the SPASM.MSE vignettes here: https://lichengxue.github.io/SPASAM.MSE/index.html

Starting with this one https://lichengxue.github.io/SPASAM.MSE/Management-Strategy-Evaluation.html

## Setup the operating model OM

Load wham and SPASAM.MSE

```{r}
library(wham)
library(SPASAM.MSE)

main.dir = here::here()
```

Basic info generation

```{r}
year_start <- 1
year_end   <- 20
MSE_years  <- 3

info <- generate_basic_info(
  n_stocks = 2,
  n_regions = 2,
  n_indices = 2,
  n_fleets = 2,
  n_seasons = 4,
  base.years = year_start:year_end,
  n_feedback_years = MSE_years,
  life_history = "medium",
  n_ages = 12,
  F_info = list(F.year1 = 0.2, Fhist = "F-H-L", Fmax = 2, Fmin = 1, change_time = 0.5),
  catch_info = list(catch_cv = 0.1, catch_Neff = 100),
  index_info = list(index_cv = 0.1, index_Neff = 100, fracyr_indices = 0.625, q = 0.2),
  fracyr_spawn = 0.625
)

basic_info = info$basic_info
catch_info = info$catch_info
index_info = info$index_info
F_info     = info$F
```

I guess we'll have movement

```{r}
basic_info <- generate_NAA_where(basic_info, move.type = 2)
move <- generate_move(
  basic_info = basic_info,
  move.type = 2,
  move.rate = c(0.3, 0.1),
  move.re = "iid_y",
  move.sigma = 0.5
)
```

and selectivity

```{r}
n_stocks  <- as.integer(basic_info['n_stocks'])
n_regions <- as.integer(basic_info['n_regions'])
n_fleets  <- as.integer(basic_info['n_fleets'])
n_indices <- as.integer(basic_info['n_indices'])
n_ages    <- as.integer(basic_info['n_ages'])

fleet_pars <- c(5, 1)
index_pars <- c(2, 1)
sel <- list(
  model = rep("logistic", n_fleets + n_indices),
  initial_pars = c(rep(list(fleet_pars), n_fleets), rep(list(index_pars), n_indices))
)
```

now the numbers at age NAA

```{r}
sigma      <- "rec+1"
re_cor     <- "iid"
ini.opt    <- "equilibrium"
alpha <- 12
beta  <- 1.5e-4

NAA_sig <- 0.2
sigma_vals <- array(NAA_sig, dim = c(n_stocks, n_regions, n_ages))
log_N1 <- rep(10, n_stocks)
N1_pars <- generate_ini_N1(basic_info, ini.opt, log_N1)

NAA_re <- list(
  N1_model = rep(ini.opt, n_stocks),
  sigma = rep(sigma, n_stocks),
  cor = rep(re_cor, n_stocks),
  recruit_model = 3,
  recruit_pars = rep(list(c(alpha, beta)), n_stocks),
  sigma_vals = sigma_vals,
  N1_pars = N1_pars
)
```

make WHAM input

```{r}
input <- prepare_wham_input(
  basic_info = basic_info,
  selectivity = sel,
  NAA_re = NAA_re,
  move = move,
  catch_info = catch_info,
  index_info = index_info,
  F = F_info
)
```

make the OM

```{r}
random = input$random # check what processes are random effects
input$random = NULL # so inner optimization won't change simulated RE
om <- fit_wham(input, do.fit = F, do.brps = T, MakeADFun.silent = TRUE)
# Note: do.fit must be FALSE (no modeling fitting yet)
```

make a dataset

```{r}
om_with_data <- update_om_fn(om, seed = 123, random = random)
```

setup assessment interval

```{r}
assess.interval <- 3 # Note: assessment interval is 3 years, given the feedback period is 3 years, there will be only 1 assessment
base.years      <- year_start:year_end # Burn-in period
first.year      <- head(base.years,1)
terminal.year   <- tail(base.years,1)
assess.years    <- seq(terminal.year, tail(om$years,1)-assess.interval,by = assess.interval)

mods <- list() # Create a list to save MSE outputs
```

## Setup and run alternative estimation models EMs

5 EMs are set up with varying degrees of spatial resolution from none to full

## EM1 is all one area for stock and fleets

```{r}
n_stocks = n_regions = n_fleets = n_indices = 1

sel_em <- list(model=rep("logistic",n_fleets+n_indices),
               initial_pars=c(rep(list(fleet_pars),n_fleets),rep(list(index_pars),n_indices)))

NAA_re_em <- list(N1_model="equilibrium",sigma="rec+1",cor="iid")

mods[[1]] = loop_through_fn(om = om_with_data,
                            em_info = info, 
                            random = random,
                            sel_em = sel_em, 
                            NAA_re_em = NAA_re_em, 
                            move_em = NULL,
                            age_comp_em = "multinomial",
                            em.opt = list(separate.em = TRUE, 
                                          separate.em.type = 1, 
                                          do.move = FALSE, 
                                          est.move = FALSE), # here to choose panmictic 
                            aggregate_catch_info = list(n_fleets = 1, 
                                                        fleet_pointer = c(1,1), 
                                                        use_catch_weighted_waa=TRUE, 
                                                        catch_Neff = 100, 
                                                        catch_cv = 0.1),
                            aggregate_index_info = list(n_indices = 1, 
                                                        index_pointer = c(1,1), 
                                                        use_catch_weighted_waa=TRUE, 
                                                        index_Neff = 100, 
                                                        index_cv = 0.1),
                            assess_years = assess.years, 
                            assess_interval = assess.interval, 
                            base_years = base.years,
                            year.use = 20, # number of years of data you want to use in the assessment model
                            seed = 123) # Must use the same seed (same as step 8) to generate random effects 
```

## EM2 is all one area for stock with fleets accounting for spatial structure

```{r}
n_stocks = n_regions = 1
n_fleets = n_indices = 2
sel_em <- list(model=rep("logistic",n_fleets+n_indices),
               initial_pars=c(rep(list(fleet_pars),n_fleets),rep(list(index_pars),n_indices)))

NAA_re_em <- list(N1_model="equilibrium",sigma="rec+1",cor="iid")

mods[[2]] = loop_through_fn(om = om_with_data, 
                            em_info = info, 
                            random = random,
                            sel_em = sel_em, 
                            NAA_re_em = NAA_re_em, 
                            move_em = NULL,
                            age_comp_em = "multinomial",
                            em.opt = list(separate.em = TRUE, 
                                          separate.em.type = 2, 
                                          do.move = FALSE, 
                                          est.move = FALSE), # option to choose spatially implicit
                            assess_years = assess.years, 
                            assess_interval = assess.interval, 
                            base_years = base.years,
                            year.use = 20, # number of years of data you want to use in the assessment model
                            seed = 123) 
```

## EM3 is separate assessments in each stock area

```{r}
n_stocks = n_regions = n_fleets = n_indices = 1

sel_em <- list(model=rep("logistic",n_fleets+n_indices),
               initial_pars=c(rep(list(fleet_pars),n_fleets),rep(list(index_pars),n_indices)))

NAA_re_em <- list(N1_model="equilibrium",sigma = "rec+1", cor="iid")

mods[[3]] = loop_through_fn(om = om_with_data, 
                            em_info = info, 
                            random = random,
                            sel_em = sel_em, 
                            NAA_re_em = NAA_re_em, 
                            move_em = NULL,
                            age_comp_em = "multinomial",
                            em.opt = list(separate.em = TRUE, 
                                          separate.em.type = 3, 
                                          do.move = FALSE, 
                                          est.move = FALSE), # option to choose separate panmictic  
                            assess_years = assess.years, 
                            assess_interval = assess.interval, 
                            base_years = base.years,
                            year.use = 20, # number of years of data you want to use in the assessment model
                            seed = 123)
```

## EM4 is disaggregated areas for the stock and fleeets no movement

```{r}
n_stocks = n_regions = n_fleets = n_indices = 2

sel_em <- list(model=rep("logistic",n_fleets+n_indices),
               initial_pars=c(rep(list(fleet_pars),n_fleets),rep(list(index_pars),n_indices)))

NAA_re_em <- list(N1_model=rep("equilibrium",n_stocks),
                  sigma=rep("rec+1",n_stocks),
                  cor=rep("iid",n_stocks),
                  recruit_model = 2)

mods[[4]] = loop_through_fn(om = om_with_data, 
                            em_info = info, 
                            random = random,
                            sel_em = sel_em, 
                            NAA_re_em = NAA_re_em, 
                            move_em = NULL,
                            age_comp_em = "multinomial",
                            em.opt = list(separate.em = FALSE, 
                                          separate.em.type = 3, 
                                          do.move = FALSE, 
                                          est.move = FALSE), # option to choose spatially disaggregated
                            assess_years = assess.years, 
                            assess_interval = assess.interval, 
                            base_years = base.years,
                            year.use = 20, # number of years of data you want to use in the assessment model
                            seed = 123)
```

## EM5 is disaggregated areas for the stock and fleeets with movement

```{r}
n_stocks = n_regions = n_fleets = n_indices = 2

sel_em <- list(model=rep("logistic",n_fleets+n_indices),
               initial_pars=c(rep(list(fleet_pars),n_fleets),rep(list(index_pars),n_indices)))

NAA_re_em <- list(N1_model=rep("equilibrium",n_stocks),
                  sigma=rep("rec+1",n_stocks),
                  cor=rep("iid",n_stocks),
                  NAA_where = basic_info$NAA_where)

# Set a prior information
move_em <- generate_move(
  basic_info = basic_info,
  move.type = 2,
  move.rate = c(0.3, 0.1),
  move.re = "iid_y",
  move.sigma = 0.5,
  prior.sigma = 0.5,
  use.prior = TRUE
)

mods[[5]] = loop_through_fn(om = om_with_data,
                            em_info = info, 
                            random = random,
                            sel_em = sel_em, 
                            NAA_re_em = NAA_re_em, 
                            move_em = move_em,
                            age_comp_em = "multinomial",
                            em.opt = list(separate.em = FALSE, 
                                          separate.em.type = 3, 
                                          do.move = TRUE,
                                          est.move = TRUE), # option to choose spatially explicit
                            assess_years = assess.years, 
                            assess_interval = assess.interval, 
                            base_years = base.years,
                            year.use = 20, # number of years of data you want to use in the assessment model
                            seed = 123)
```

## Comparisons among EMs

```{r}
library(ggplot2)
library(dplyr)

yrs <- 14:23

# --------------------------
# Build dataframe
# --------------------------
plot_df <- do.call(rbind, lapply(seq_along(mods), function(i) {
  
  data.frame(
    Year = rep(yrs, 2),
    Value = c(
      mods[[i]]$om$rep$SSB[yrs,1],
      mods[[i]]$om$rep$pred_catch[yrs,1]
    ),
    Metric = rep(c("SSB", "Catch"), each = length(yrs)),
    EM = paste0("EM ", i)
  )
  
}))

# --------------------------
# Plot
# --------------------------
ggplot(plot_df, aes(x = Year, y = Value, color = EM)) +
  geom_line(linewidth = 1.2) +
  facet_wrap(~Metric, scales = "free_y") +
  labs(
    x = "Year",
    y = NULL,
    color = "Estimation Model"
  ) +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 13),
    legend.position = "top",
    legend.title = element_text(face = "bold"),
    axis.title = element_text(face = "bold")
  ) +
  scale_color_brewer(palette = "Set1")
```

